\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,            % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[colorlinks=true, linkcolor=black, urlcolor=blue]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering
\usepackage{comment}                % block comment

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=6pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Thuy Nguyen}

\vspace{5pt}

% contact information
\centerline{\href{mailto:thuybohr@gmail.com}{thuybohr@gmail.com} | 206-423-9827 |
\href{https://www.linkedin.com/in/thuy-nguyen-46505121b/}{linkedin.com/in/thuy-nguyen-46505121b}}

\centerline{\href{https://github.com/Monica20030707}{github.com/Monica20030707} | 
\href{https://monica20030707.github.io/}{monica20030707.github.io/}} 

\vspace{-9pt}

% education section
\section*{Education}
\textbf{Bellevue College} -- BS in Computer Science -- 3.6 GPA \hfill September 2021 -- June 2025\\
\vspace{-9pt}
\begin{itemize}
  \item Award: Amazon Scholarship, Activities: Social Media Manager of Computer Science Club
\end{itemize}

\vspace{-18.5pt}

% experience section
\section*{Experience}

\textbf{Sales Specialist,} {Verizon} -- Covington, WA \hfill November 2025 -- Current \\
\vspace{-9pt}
\begin{itemize}
  \item Consistently surpassed monthly sales quotas by achieving 130\% of targets through technical product expertise and consultative solution-selling.
  \item De-escalated complex technical issues by explaining bandwidth optimization, signal propagation, and network topology to non-technical customers.
  \item Developed ongoing relationships with strategic business partners by identifying their long-term growth potential and tailoring technical solutions to their specific needs.
\end{itemize}

\textbf{Associate Full Stack Developer,} {Forge Tek Studios} -- Remote \hfill August 2025 -- Current 
\vspace{-9pt}
\begin{itemize}
  \item Owned the end-to-end development and deployment lifecycle of full-stack projects, ensuring high standards for code quality and performance with minimal supervision.
  \item Architected modular React systems and optimized data synchronization logic, reducing ingestion overhead by 80\% for high-traffic environments.
  \item Collaborated across teams to map complex requirements to scalable technical solutions, advocating for architecture that balances cost and performance.
\end{itemize}

\textbf{Teaching Assistant,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- December 2024 \\
\vspace{-9pt}
\begin{itemize}
  \item Provided in-depth technical coaching and workshops on relational schema design and optimization for a classroom of 40+ students.
  \item Mentored students on software engineering principles and documentation, improving overall proficiency and project success rates by 20\%.
  \item Adapted communication methods to suit diverse technical backgrounds, ensuring clear understanding of foundational engineering concepts.
\end{itemize}

\begin{comment}
\textbf{Full Stack Developer Intern,} {METY Technology} -- Remote \hfill September 2024 -- June 2025 
\vspace{-9pt}
\begin{itemize}
  \item Engineered a real-time, interaction-driven application using React and TensorFlow.js (MoveNet), processing live camera input and rendering responsive UI feedback.
  \item Developed secure and scalable RESTful APIs with Express.js and Node.js to manage data flow and backend communication.
  \item Built and maintained a CI/CD pipeline using AWS Amplify, with automated testing via Jest and code quality enforcement through ESLint.
\end{itemize}
\end{comment}

\vspace{-18.5pt}

% projects section
\section*{Projects}

\textbf{Network-Wide Ad Blocker (Pi-hole)}{ - Shell, Linux, Raspberry Pi, DNS} \hfill \href{https://github.com/Monica20030707}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Engineered a custom network-layer security solution using Linux and Pi-hole to filter DNS traffic across all connected devices.
  \item Diagnosed and resolved network routing conflicts to ensure zero-latency ad blocking and stable network performance.
  \item Independently researched and implemented a home-lab solution for enhanced personal data privacy and network-wide security.
\end{itemize}

\textbf{Stock Ratio Tracker}{ - Python, React, Typescript, Perspective} \hfill \href{https://github.com/Monica20030707/tradingDashboard-UI}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Architected the data-flow pipeline connecting Python backend calculations to a live React dashboard, ensuring low-latency updates. 
  \item Integrated JPMorgan Chase’s Perspective library to generate interactive graphs for real-time monitoring of financial metrics.
  \item Optimized data streaming and state synchronization between backend processes and visualization components to increase decision-making efficiency.
\end{itemize}

\vspace{-18.5pt}


% skills section
\section*{Skills}
\textbf{Languages:} Python, TypeScript, Java, SQL (MySQL), JavaScript, Go, C++, Shell Scripting, HTML/CSS\\
\textbf{Skills:} Technical Sales, Customer Relations, Account Management, Troubleshooting, Data Visualization, Full-stack\\
\textbf{Tools:} Linux, Raspberry Pi, Networking (DNS), React, Node.js, AWS, Docker, Git, Perspective, Microsoft Teams\\

\vspace{-6.5pt}

\end{document}
