\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,            % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[colorlinks=true, linkcolor=black, urlcolor=blue]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering
\usepackage{comment}                % block comment

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=6pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Thuy Nguyen}

\vspace{5pt}

% contact information
\centerline{\href{mailto:thuybohr@gmail.com}{thuybohr@gmail.com} | 206-423-9827 |
\href{https://www.linkedin.com/in/thuy-nguyen-46505121b/}{linkedin.com/in/thuy-nguyen-46505121b}}

\centerline{\href{https://github.com/Monica20030707}{github.com/Monica20030707} | 
\href{https://monica20030707.github.io/}{monica20030707.github.io/}} 

\vspace{-9pt}

% education section
\section*{Education}
\textbf{Bellevue College} -- BS in Computer Science -- 3.6 GPA \hfill September 2021 -- June 2025\\
\vspace{-9pt}
\begin{itemize}
  \item Award: Amazon Scholarship, Activities: Social Media Manager of Computer Science Club
\end{itemize}

\vspace{-18.5pt}

% experience section
\section*{Experience}

\textbf{Sales Specialist,} {Verizon} -- Covington, WA \hfill November 2025 -- Current \\
\vspace{-9pt}
\begin{itemize}
  \item Consistently surpassed monthly sales quotas by achieving 130\% of targets through technical product expertise and consultative solution-selling.
  \item Developed ongoing relationships with strategic business partners by identifying their long-term growth potential and tailoring technical solutions to their specific needs.
  \item De-escalated complex technical issues by explaining bandwidth optimization, signal propagation, and network topology to non-technical customers.
\end{itemize}

\textbf{Associate Full Stack Developer,} {Forge Tek Studios} -- Remote \hfill August 2025 -- Current 
\vspace{-9pt}
\begin{itemize}
  \item Architected a modular React frontend with a serverless backend, leveraging custom hooks and context for efficient state management and performance.
  \item Implemented dynamic data fetching and caching strategies for third-party APIs like Steam and Fab Marketplace to reduce latency and improve user experience.
  \item Reduced system load and data ingestion overhead by 80\% through optimization of client-side rendering and synchronization logic.
\end{itemize}

\begin{comment}
\textbf{Full Stack Developer Intern,} {METY Technology} -- Remote \hfill September 2024 -- June 2025 
\vspace{-9pt}
\begin{itemize}
  \item Engineered a real-time, interaction-driven application using React and TensorFlow.js (MoveNet), processing live camera input and rendering responsive UI feedback.
  \item Developed secure and scalable RESTful APIs with Express.js and Node.js to manage data flow and backend communication, in frontend, used Tailwind CSS for styling and Redux Toolkits for state managing.
  \item Built and maintained a CI/CD pipeline using AWS Amplify, with automated testing via Jest and code quality enforcement through ESLint.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Open-Source Intern,} {CodeDay} -- Seattle, WA \hfill April 2025 -- May 2025 \\
\vspace{-9pt}
\begin{itemize}
  \item Led team progress as Scrum Master, ensuring timely delivery by coordinating client communications.
  \item Resolved two OED tickets in Agile, through the implementation of database test cases.
  \item Ran and tested the website in various environments with Docker, ensuring its functionality and performance.
\end{itemize}
\end{comment}

\textbf{Teaching Assistant,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- December 2024 \\
\vspace{-9pt}
\begin{itemize}
  \item Provided in-depth technical coaching on relational schema design, query optimization, and Java unit testing patterns for over 40 students.
  \item Facilitated workshops on MySQL Workbench for database visualization and management, enhancing foundational programming skills.
  \item Improved student success rates by 20\% through targeted feedback and supplemental instruction in software engineering best practices.
\end{itemize}

\begin{comment}
\textbf{Coding Competition Developer,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- May 2025 \\
\vspace{-9pt}
\begin{itemize}
  \item Developed real-time score updates using SQL and PHP, increasing efficiency by 40\%.
  \item Enhanced web interfaces with HTML and CSS, boosting user satisfaction by 30\%.
  \item Created coding problems with auto test cases for Java, Python, C++, and Golang.
  \item Assisted onsite at a competition with 30+ participants to ensure smooth operations.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Web Design Intern,} {RSVP} -- Sai Gon, Vietnam \hfill July 2022 -- September 2022 \\
\vspace{-9pt}
\begin{itemize}
  \item Designed a Figma mock-up for the company's planned landing page refresh.
  \item Collaborated in a team of 4 developers, handled minor coding tickets and assisted with design works.
  \item Worked closely with clients to ensure our HTML email template suited the clients needs.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Front Desk Assistant} {, Public Safety Department, Bellevue College} -- Bellevue, WA \hfill June 2023 -- August 2023 \\
\vspace{-9pt}
\begin{itemize}
  \item Managed tasks with precision in a fast-paced environment.
  \item Using Canva to design Parking Bookmark for advertising \& assisting users.
  \item Utilized Microsoft Word, Excel and Outlook for efficient data management.
  \item Collaborated with team members to ensure accurate and prompt assistance.
\end{itemize}
\end{comment}

\vspace{-18.5pt}

% projects section
\section*{Projects}

\textbf{Network-Wide Ad Blocker (Pi-hole)}{ - Linux, DNS, Shell Scripting} \hfill \href{https://github.com/Monica20030707}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Engineered a custom network-layer security solution using Linux and Pi-hole to filter DNS traffic across all connected devices, enhancing network privacy.
  \item Enhanced network-wide security and reduced bandwidth consumption by filtering malicious and tracking-heavy domains, improving page load speeds by 30\%.
\end{itemize}

\begin{comment}
\textbf{Stock Ratio Tracker}{ - Python, React, Typescript} \hfill \href{https://github.com/Monica20030707/tradingDashboard-UI}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Architected the data-flow pipeline connecting Python backend calculations to a live React dashboard, ensuring stable, low-latency ratio updates. 
  \item Used JPMorgan Chase’s open-source library called Perspective to generate a live graph that displays a data feed in a clear and visually appealing way for traders to monitor.
  \item Implemented automated unit tests to ensure correctness and reliability.
\end{itemize}
\end{comment}

\textbf{Stock Ratio Tracker}{ - Python, React, Perspective} \hfill \href{https://github.com/Monica20030707/tradingDashboard-UI}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Built a Python-based data ingestion and transformation layer to feed live financial metrics into a React-based frontend via high-performance streaming.
  \item Increased trader decision-making efficiency by 40\% through intuitive, real-time dashboard design and optimized state synchronization.
\end{itemize}


\begin{comment}
\textbf{Read MNIST Handwritten Dataset}{ - Python, Numpy Library} \hfill \href{https://github.com/Monica20030707/Artificial-Neutral-Network_ML}{github.com} \\
\vspace{-9pt}
\begin{itemize} 
  \item Built an Artificial Neural Network (ANN) from scratch to classify handwritten digits (0-9). 
  \item Achieved over 90\% accuracy using Backpropagation algorithm.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Reverse-Polish Calculator}{ - Java, ANTLR, JUnit, OOP Concepts} \hfill \href{https://github.com/Monica20030707/reverse-Polish_calculator}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Applied the Visitor design pattern to traverse ASTs and evaluate expressions, reinforcing compiler theory and object-oriented programming concepts.
  \item Leveraged stacks and tree-based data structures to correctly parse and compute reverse-polish expressions.
  \item Implemented automated unit tests to ensure correctness and reliability of expression evaluation.
\end{itemize}
\end{comment}


\begin{comment}
\textbf{Traffic Violation Detection System}{ - Javascript, AWS Cloud Services} \hfill \href{https://github.com/Monica20030707/AWS_rekonigition-N-read-database}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Processed license plate images from S3, sending email notices to offenders with violation details and fines.
  \item Engineered Regex to identify California plates, routed through SQS and EventBridge for proper handling.
\end{itemize}
\end{comment}

% alternate formatting for projects section
\begin{comment}
% \begin{itemize}
%   \item \textbf{QuantSoftware Toolkit:} Open source Python library for data analysis and machine learning for finance
%   \item \textbf{GitHub Visualization:} Data visualization of Git Log data using D3 to analyze project trends over time
%   \item \textbf{Recommendation System:} Music and movie recommender systems using collaborative filtering on public datasets
%   \item \textbf{Mac Setup:} Book that gives step by step instructions on setting up developer environment on Mac OS
% \end{itemize}
\end{comment}

\vspace{-18.5pt}


% skills section
\section*{Skills}
\textbf{Languages:} Python, SQL, TypeScript, Java, JavaScript, Shell Scripting, MySQL, HTML/CSS\\
\textbf{Skills:} RESTful APIs, Technical Troubleshooting, Customer Relations, Consultative Selling, API Integration, Linux, DNS\\
\textbf{Tools:} React, Node.js, Perspective, Raspberry Pi, AWS Cloud Services, Git, Docker, CRM, Jira\\

\vspace{-6.5pt}

\end{document}
