\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,            % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[colorlinks=true, linkcolor=black, urlcolor=blue]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering
\usepackage{comment}                % block comment

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=6pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Thuy Nguyen}

\vspace{5pt}

% contact information
\centerline{\href{mailto:thuybohr@gmail.com}{thuybohr@gmail.com} | 206-423-9827 |
\href{https://www.linkedin.com/in/thuy-nguyen-46505121b/}{linkedin.com/in/thuy-nguyen-46505121b}}

\centerline{\href{https://github.com/Monica20030707}{github.com/Monica20030707} | 
\href{https://monica20030707.github.io/}{monica20030707.github.io/}} 

\vspace{-9pt}

% education section
\section*{Education}
\textbf{Bellevue College} -- BS in Computer Science -- 3.6 GPA \hfill September 2021 -- June 2025\\
\vspace{-9pt}
\begin{itemize}
  \item Award: Amazon Scholarship, Activities: Social Media Manager of Computer Science Club
\end{itemize}

\vspace{-18.5pt}

% experience section
\section*{Experience}

\textbf{Sales Specialist,} {Verizon} -- Covington, WA \hfill November 2025 -- Current \\
\vspace{-9pt}
\begin{itemize}
  \item Consistently surpassed monthly sales quotas by achieving 130\% of targets through technical product expertise and consultative solution-selling.
  \item Contributed to regional sales targets by translating technical specifications into business value for diverse customer segments.
  \item Streamlined inventory workflows and device diagnostic processes, reducing customer wait times and improving store operational efficiency.
\end{itemize}

\textbf{Associate Full Stack Developer,} {Forge Tek Studios} -- Remote \hfill August 2025 -- Current 
\vspace{-9pt}
\begin{itemize}
  \item Built and deployed a production-ready full-stack application integrating e-commerce APIs (Steam, Fab Marketplace) to dynamically render content.
  \item Reduced system load and data ingestion overhead by 80\% through optimization of client-side rendering and synchronization logic.
  \item Managed the full production release lifecycle, ensuring a high-performance experience for users across digital marketplaces.
\end{itemize}

\textbf{Open-Source Intern (Scrum Master),} {CodeDay} -- Seattle, WA \hfill April 2025 -- May 2025 \\
\vspace{-9pt}
\begin{itemize}
  \item Drove project velocity as Scrum Master, meeting all client deadlines through proactive blocker removal and cross-functional communication.
  \item Facilitated daily stand-ups and retrospectives, aligning a distributed team on weekly sprint goals and deliverable timelines.
  \item Collaborated directly with stakeholders to clarify requirements and translate them into actionable development tasks.
\end{itemize}

\textbf{Front Desk Assistant} {, Public Safety Department, Bellevue College} -- Bellevue, WA \hfill June 2023 -- August 2023 \\
\vspace{-9pt}
\begin{itemize}
  \item Managed administrative workflows with precision in a high-volume, fast-paced environment.
  \item Utilized Microsoft Excel and Outlook for efficient data management and appointment scheduling.
  \item Collaborated with team members to ensure accurate information delivery and prompt customer assistance.
\end{itemize}

\begin{comment}
\textbf{Full Stack Developer Intern,} {METY Technology} -- Remote \hfill September 2024 -- June 2025 
\vspace{-9pt}
\begin{itemize}
  \item Engineered a real-time, interaction-driven application using React and TensorFlow.js (MoveNet), processing live camera input and rendering responsive UI feedback.
  \item Developed secure and scalable RESTful APIs with Express.js and Node.js to manage data flow and backend communication.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Teaching Assistant,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- December 2024 \\
\vspace{-9pt}
\begin{itemize}
  \item Guided 40+ students in Java and SQL, providing in-depth technical coaching on schema design and debugging patterns.
  \item Improved student success rates by 20\% through targeted feedback and supplemental instruction in technical best practices.
\end{itemize}
\end{comment}

\vspace{-18.5pt}

% projects section
\section*{Projects}

\textbf{Stock Ratio Tracker}{ - Python, React, Typescript} \hfill \href{https://github.com/Monica20030707/tradingDashboard-UI}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Architected the data-flow pipeline connecting Python backend calculations to a live React dashboard, ensuring stable, low-latency updates. 
  \item Built an intuitive, real-time visualization tool for monitoring financial metrics, increasing decision-making efficiency.
\end{itemize}

\textbf{Traffic Violation Detection System}{ - Javascript, AWS Cloud Services} \hfill \href{https://github.com/Monica20030707/AWS_rekonigition-N-read-database}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Engineered an automated serverless pipeline on AWS, integrating machine learning for image analysis and SQS for event-driven message processing.
  \item Reduced manual notification processing time by 90\% through automated regex-based data extraction and routing.
\end{itemize}

\vspace{-18.5pt}

% skills section
\section*{Skills}
\textbf{Languages:} SQL (MySQL), Python, JavaScript, TypeScript, Java, C++, HTML/CSS, Shell Scripting\\
\textbf{Skills:} Outbound Sales, Pipeline Management, CRM (Salesforce), KPIs, Agile/Scrum, Business Analysis\\
\textbf{Tools:} Salesforce, G-Suite, Microsoft Excel, Microsoft Outlook, Slack, AWS, Docker, React, Node.js\\

\vspace{-6.5pt}

\end{document}
