\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,            % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[colorlinks=true, linkcolor=black, urlcolor=blue]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering
\usepackage{comment}                % block comment

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=6pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Thuy Nguyen}

\vspace{5pt}

% contact information
\centerline{\href{mailto:thuybohr@gmail.com}{thuybohr@gmail.com} | 206-423-9827 |
\href{https://www.linkedin.com/in/thuy-nguyen-46505121b/}{linkedin.com/in/thuy-nguyen-46505121b}}

\centerline{\href{https://github.com/Monica20030707}{github.com/Monica20030707} | 
\href{https://monica20030707.github.io/}{monica20030707.github.io/}} 

\vspace{-9pt}

% education section
\section*{Education}
\textbf{Bellevue College} -- BS in Computer Science -- 3.6 GPA \hfill September 2021 -- June 2025\\
\vspace{-9pt}
\begin{itemize}
  \item Award: Amazon Scholarship, Activities: Social Media Manager of Computer Science Club
\end{itemize}

\vspace{-18.5pt}

% experience section
\section*{Experience}

\textbf{Associate Full Stack Developer,} {Forge Tek Studios} -- Remote \hfill August 2025 -- Current 
\vspace{-9pt}
\begin{itemize}
  \item Optimized client-side rendering and data synchronization for a production React application, reducing load and ingestion overhead by 80\%—focusing on performance-sensitive UI updates.
  \item Architected a modular React frontend with a serverless backend, leveraging custom hooks and context for efficient state management and low-latency API integration.
  \item Owned the end-to-end development and deployment lifecycle, ensuring high standards for code quality, application performance, and stable production environments.
\end{itemize}

\textbf{Full Stack Developer Intern,} {METY Technology} -- Remote \hfill September 2024 -- June 2025 
\vspace{-9pt}
\begin{itemize}
  \item Integrated real-time machine learning models (MoveNet) with React to enable low-latency user interaction, processing live camera input directly in the browser.
  \item Automated testing and deployment processes via a custom CI/CD pipeline on AWS Amplify, ensuring consistent delivery and high quality standards through Jest and ESLint.
  \item Developed secure and scalable RESTful APIs with Express.js and Node.js to manage real-time data flow and backend communication.
\end{itemize}

\textbf{Sales Specialist,} {Verizon} -- Covington, WA \hfill November 2025 -- Current \\
\vspace{-9pt}
\begin{itemize}
  \item Consistently surpassed monthly sales quotas by achieving 130\% of targets through technical product expertise and consultative solution-selling for complex consumer and SMB needs.
  \item De-escalated complex technical issues by explaining bandwidth optimization, signal propagation, and network topology to non-technical customers, translating technical value into business value.
  \item Conducted hardware diagnostics and firmware validation on mobile devices and networking equipment to ensure optimal performance and customer satisfaction.
\end{itemize}

\textbf{Teaching Assistant,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- December 2024 \\
\vspace{-9pt}
\begin{itemize}
  \item Provided in-depth technical coaching on relational schema design, query optimization, and Java unit testing patterns to a classroom of 40+ students.
  \item Improved student success rates by 20\% through targeted feedback and supplemental instruction in technical best practices and debugging methodologies.
  \item Facilitated workshops on MySQL Workbench for database visualization, helping students master complex software systems and infrastructure.
\end{itemize}

\begin{comment}
\textbf{Open-Source Intern (Scrum Master),} {CodeDay} -- Seattle, WA \hfill April 2025 -- May 2025 \\
\vspace{-9pt}
\begin{itemize}
  \item Facilitated daily stand-ups and retrospectives as Scrum Master, aligning a cross-functional team on weekly sprint goals.
  \item Authored comprehensive database integration tests to resolve high-priority open-source tickets and prevent regression.
\end{itemize}
\end{comment}

\vspace{-18.5pt}

% projects section
\section*{Projects}

\textbf{Traffic Violation Detection System}{ - JavaScript, AWS Cloud Services} \hfill \href{https://github.com/Monica20030707/AWS_rekonigition-N-read-database}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Architected an event-driven serverless pipeline on AWS, integrating Rekognition for image analysis and SQS for decoupled message processing.
  \item Automated the violation detection and notification workflow, reducing manual processing time by over 90\% through event-driven logic and AWS Lambda.
\end{itemize}

\textbf{Stock Ratio Tracker}{ - Python, React, TypeScript} \hfill \href{https://github.com/Monica20030707/tradingDashboard-UI}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Built a Python-based data ingestion and transformation layer to feed live financial metrics into a React-based frontend for real-time monitoring.
  \item Optimized real-time data streaming and state synchronization between Python processes and high-performance streaming visualization components.
\end{itemize}

\vspace{-18.5pt}

% skills section
\section*{Skills}
\textbf{Languages:} SQL (MySQL), Python, JavaScript, TypeScript, Java, C++, HTML/CSS, Shell Scripting (Bash)\\
\textbf{Skills:} Cloud Computing (AWS), Observability/Monitoring, APM, Technical Troubleshooting, RESTful APIs, CLI\\
\textbf{Tools:} AWS (Rekognition, SQS, S3, EventBridge), React, Node.js, Docker, Git, MySQL Workbench, Jest\\

\vspace{-6.5pt}

\end{document}
