\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,            % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[colorlinks=true, linkcolor=black, urlcolor=blue]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering
\usepackage{comment}                % block comment

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=6pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Thuy Nguyen}

\vspace{5pt}

% contact information
\centerline{\href{mailto:thuybohr@gmail.com}{thuybohr@gmail.com} | 206-423-9827 |
\href{https://www.linkedin.com/in/thuy-nguyen-46505121b/}{linkedin.com/in/thuy-nguyen-46505121b}}

\centerline{\href{https://github.com/Monica20030707}{github.com/Monica20030707} | 
\href{https://monica20030707.github.io/}{monica20030707.github.io/}} 

\vspace{-9pt}

% education section
\section*{Education}
\textbf{Bellevue College} -- BS in Computer Science -- 3.6 GPA \hfill September 2021 -- June 2025\\
\vspace{-9pt}
\begin{itemize}
  \item Award: Amazon Scholarship, Activities: Social Media Manager of Computer Science Club
\end{itemize}

\vspace{-18.5pt}

% experience section
\section*{Experience}

\textbf{Sales Specialist,} {Verizon} -- Covington, WA \hfill November 2025 -- Current \\
\vspace{-9pt}
\begin{itemize}
  \item Consistently surpassed monthly sales quotas by achieving 130\% of targets through technical product expertise and consultative solution-selling.
  \item De-escalated complex technical issues by explaining bandwidth optimization, signal propagation, and network topology to non-technical customers.
  \item Contributed to regional sales targets by translating technical specifications into business value for diverse customer segments.
\end{itemize}

\textbf{Associate Full Stack Developer,} {Forge Tek Studios} -- Remote \hfill August 2025 -- Current 
\vspace{-9pt}
\begin{itemize}
  \item Architected a modular React frontend with a serverless backend, ensuring high standards for performance-sensitive UI updates and real-time content rendering.
  \item Reduced system load and data ingestion overhead by 80\% through optimization of client-side rendering and synchronization logic.
  \item Collaborated on design and architecture decisions, advocating for serverless solutions to meet scalability and cost requirements for high-traffic applications.
\end{itemize}

\textbf{Full Stack Developer Intern,} {METY Technology} -- Remote \hfill September 2024 -- June 2025 
\vspace{-9pt}
\begin{itemize}
  \item Engineered a real-time, interaction-driven application using React and TensorFlow.js, processing live camera input and rendering responsive UI feedback.
  \item Enhanced user engagement by 25\% through the development of highly responsive and intuitive real-time visual feedback systems.
  \item Automated testing and deployment processes via a custom CI/CD pipeline on AWS Amplify, ensuring consistent delivery and quality standards.
\end{itemize}

\begin{comment}
\textbf{Open-Source Intern,} {CodeDay} -- Seattle, WA \hfill April 2025 -- May 2025 \\
\vspace{-9pt}
\begin{itemize}
  \item Led team progress as Scrum Master, ensuring timely delivery by coordinating client communications.
  \item Resolved two OED tickets in Agile, through the implementation of database test cases.
  \item Ran and tested the website in various environments with Docker, ensuring its functionality and performance.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Teaching Assistant,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- December 2024 \\
\vspace{-9pt}
\begin{itemize}
  \item Guided 40+ students in Java and SQL, with class materials during and after class.
  \item Educated students in relational database design and MySQL Workbench operations.
  \item Elevated student proficiency in JUnit and Javadoc, enhancing assignment quality by 20\%.
\end{itemize}
\end{comment}

\textbf{Coding Competition Developer,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- May 2025 \\
\vspace{-9pt}
\begin{itemize}
  \item Directed onsite technical operations for 30+ participants, ensuring a seamless competition experience and providing immediate troubleshooting support.
  \item Built a dynamic leaderboard system using PHP and SQL for real-time performance tracking during competitive coding events.
  \item Authored automated test cases across 5 languages to validate participant submissions for algorithm accuracy and efficiency.
\end{itemize}

\begin{comment}
\textbf{Web Design Intern,} {RSVP} -- Sai Gon, Vietnam \hfill July 2022 -- September 2022 \\
\vspace{-9pt}
\begin{itemize}
  \item Designed a Figma mock-up for the company's planned landing page refresh.
  \item Collaborated in a team of 4 developers, handled minor coding tickets and assisted with design works.
  \item Worked closely with clients to ensure our HTML email template suited the clients needs.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Front Desk Assistant} {, Public Safety Department, Bellevue College} -- Bellevue, WA \hfill June 2023 -- August 2023 \\
\vspace{-9pt}
\begin{itemize}
  \item Managed tasks with precision in a fast-paced environment.
  \item Using Canva to design Parking Bookmark for advertising \& assisting users.
  \item Utilized Microsoft Word, Excel and Outlook for efficient data management.
  \item Collaborated with team members to ensure accurate and prompt assistance.
\end{itemize}
\end{comment}

\vspace{-18.5pt}

% projects section
\section*{Projects}

\textbf{Stock Ratio Tracker}{ - Python, React, Typescript} \hfill \href{https://github.com/Monica20030707/tradingDashboard-UI}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Architected the data-flow pipeline connecting Python backend calculations to a live React dashboard, ensuring stable, low-latency ratio updates. 
  \item Increased trader decision-making efficiency by 40\% through intuitive, real-time dashboard design and high-performance streaming libraries.
  \item Optimized real-time data streaming and state synchronization between Python processes and Perspective visualization components.
\end{itemize}

\begin{comment}
\textbf{Read MNIST Handwritten Dataset}{ - Python, Numpy Library} \hfill \href{https://github.com/Monica20030707/Artificial-Neutral-Network_ML}{github.com} \\
\vspace{-9pt}
\begin{itemize} 
  \item Built an Artificial Neural Network (ANN) from scratch to classify handwritten digits (0-9). 
  \item Achieved over 90\% accuracy using Backpropagation algorithm.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Reverse-Polish Calculator}{ - Java, ANTLR, JUnit, OOP Concepts} \hfill \href{https://github.com/Monica20030707/reverse-Polish_calculator}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Applied the Visitor design pattern to traverse ASTs and evaluate expressions, reinforcing compiler theory and object-oriented programming concepts.
  \item Leveraged stacks and tree-based data structures to correctly parse and compute reverse-polish expressions.
  \item Implemented automated unit tests to ensure correctness and reliability of expression evaluation.
\end{itemize}
\end{comment}


\textbf{Traffic Violation Detection System}{ - Javascript, AWS Cloud Services} \hfill \href{https://github.com/Monica20030707/AWS_rekonigition-N-read-database}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Processed license plate images from S3 using AWS Rekognition, sending email notices to offenders with violation details and fines via automated workflows.
  \item Engineered Regex to identify California plates and routed data through SQS and EventBridge for scalable, reliable handling.
\end{itemize}

\begin{comment}
\textbf{Network-Wide Ad Blocker (Pi-hole)}{ - Raspberry Pi, Linux, DNS} \hfill \href{https://github.com/Monica20030707}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Engineered a custom network-layer security solution using Linux and Pi-hole to filter DNS traffic across all connected devices.
  \item Enhanced network-wide security and reduced bandwidth consumption by filtering malicious and tracking-heavy domains.
  \item Improved page load speeds by 30\% through proactive ad blocking and DNS caching.
\end{itemize}
\end{comment}

% alternate formatting for projects section
\begin{comment}
% \begin{itemize}
%   \item \textbf{QuantSoftware Toolkit:} Open source Python library for data analysis and machine learning for finance
%   \item \textbf{GitHub Visualization:} Data visualization of Git Log data using D3 to analyze project trends over time
%   \item \textbf{Recommendation System:} Music and movie recommender systems using collaborative filtering on public datasets
%   \item \textbf{Mac Setup:} Book that gives step by step instructions on setting up developer environment on Mac OS
% \end{itemize}
\end{comment}

\vspace{-18.5pt}


% skills section
\section*{Skills}
\textbf{Languages:} Python, TypeScript, SQL, PHP, JavaScript, Java, C++, Shell Scripting, HTML/CSS\\
\textbf{Skills:} Pre-sales Engineering, Technical Discovery, Solution Design, Product Demos, Full-stack Development, RESTful APIs\\
\textbf{Tools:} React, Node.js, AWS Cloud Services, TensorFlow.js, Perspective (JPMorgan), CRM Systems, Git, Docker\\

\vspace{-6.5pt}

\end{document}
