\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,            % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[colorlinks=true, linkcolor=black, urlcolor=blue]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering
\usepackage{comment}                % block comment

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=6pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Thuy Nguyen}

\vspace{5pt}

% contact information
\centerline{\href{mailto:thuybohr@gmail.com}{thuybohr@gmail.com} | 206-423-9827 |
\href{https://www.linkedin.com/in/thuy-nguyen-46505121b/}{linkedin.com/in/thuy-nguyen-46505121b}}

\centerline{\href{https://github.com/Monica20030707}{github.com/Monica20030707} | 
\href{https://monica20030707.github.io/}{monica20030707.github.io/}} 

\vspace{-9pt}

% education section
\section*{Education}
\textbf{Bellevue College} -- BS in Computer Science -- 3.6 GPA \hfill September 2021 -- June 2025\\
\vspace{-9pt}
\begin{itemize}
  \item Award: Amazon Scholarship, Activities: Social Media Manager of Computer Science Club
\end{itemize}

\vspace{-18.5pt}

% experience section
\section*{Experience}

\textbf{Associate Full Stack Developer,} {Forge Tek Studios} -- Remote \hfill August 2025 -- Current 
\vspace{-9pt}
\begin{itemize}
  \item Architected a modular React frontend with a serverless backend, leveraging custom hooks and context for efficient state management in a production-ready application.
  \item Implemented dynamic data fetching and caching strategies for third-party APIs like Steam and Fab Marketplace to reduce latency and improve responsive UI updates.
  \item Optimized client-side rendering and data synchronization, reducing load and ingestion overhead by 80\%—focusing on performance-sensitive systems.
\end{itemize}

\textbf{Full Stack Developer Intern,} {METY Technology} -- Remote \hfill September 2024 -- June 2025 
\vspace{-9pt}
\begin{itemize}
  \item Integrated real-time machine learning models (MoveNet) with React and TensorFlow.js to enable low-latency, gesture-based user interaction directly in the browser.
  \item Architected a secure backend using Express.js and Node.js with a robust state management layer using Redux Toolkit to manage complex data flows.
  \item Built and maintained a CI/CD pipeline using AWS Amplify, with automated testing via Jest and code quality enforcement through ESLint.
\end{itemize}

\begin{comment}
\textbf{Sales Specialist,} {Verizon} -- Covington, WA \hfill November 2025 -- Current \\
\vspace{-9pt}
\begin{itemize}
  \item Consistently surpassed monthly sales quotas by achieving 130\% of targets through technical product expertise and consultative solution-selling.
  \item Translated technical specifications into business value for diverse customer segments.
\end{itemize}
\end{comment}

\textbf{Open-Source Intern,} {CodeDay} -- Seattle, WA \hfill April 2025 -- May 2025 \\
\vspace{-9pt}
\begin{itemize}
  \item Led team progress as Scrum Master in an Agile environment, ensuring timely delivery by coordinating client communications and sprint milestones.
  \item Resolved complex backend tickets by implementing robust database test cases and ensuring data integrity across multiple environments.
  \item Orchestrated and tested web services in containerized environments with Docker, ensuring cross-platform functionality and performance.
\end{itemize}

\begin{comment}
\textbf{Teaching Assistant,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- December 2024 \\
\vspace{-9pt}
\begin{itemize}
  \item Guided 40+ students in Java and SQL, with class materials during and after class.
  \item Educated students in relational database design and MySQL Workbench operations.
  \item Elevated student proficiency in JUnit and Javadoc, enhancing assignment quality by 20\%.
\end{itemize}
\end{comment}

\textbf{Coding Competition Developer,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- May 2025 \\
\vspace{-9pt}
\begin{itemize}
  \item Built a dynamic leaderboard system using PHP and SQL for real-time performance tracking and automated score updates during competitive coding events.
  \item Authored automated test cases across Java, Python, C++, and Golang to validate participant submissions for algorithm accuracy and efficiency.
  \item Directed onsite technical operations for 30+ participants, ensuring a seamless competition experience and stable infrastructure.
\end{itemize}

\begin{comment}
\textbf{Web Design Intern,} {RSVP} -- Sai Gon, Vietnam \hfill July 2022 -- September 2022 \\
\vspace{-9pt}
\begin{itemize}
  \item Designed a Figma mock-up for the company's planned landing page refresh.
  \item Collaborated in a team of 4 developers, handled minor coding tickets and assisted with design works.
  \item Worked closely with clients to ensure our HTML email template suited the clients needs.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Front Desk Assistant} {, Public Safety Department, Bellevue College} -- Bellevue, WA \hfill June 2023 -- August 2023 \\
\vspace{-9pt}
\begin{itemize}
  \item Managed tasks with precision in a fast-paced environment.
  \item Using Canva to design Parking Bookmark for advertising \& assisting users.
  \item Utilized Microsoft Word, Excel and Outlook for efficient data management.
  \item Collaborated with team members to ensure accurate and prompt assistance.
\end{itemize}
\end{comment}

\vspace{-18.5pt}

% projects section
\section*{Projects}

\textbf{Stock Ratio Tracker}{ - Python, React, Typescript} \hfill \href{https://github.com/Monica20030707/tradingDashboard-UI}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Built a Python-based data ingestion and transformation layer to feed live financial metrics into a React-based frontend via low-latency pipelines.
  \item Optimized real-time data streaming and state synchronization between backend calculations and high-performance Perspective visualization components.
  \item Implemented automated unit tests to ensure correctness and reliability of complex ratio calculations.
\end{itemize}

\begin{comment}
\textbf{Read MNIST Handwritten Dataset}{ - Python, Numpy Library} \hfill \href{https://github.com/Monica20030707/Artificial-Neutral-Network_ML}{github.com} \\
\vspace{-9pt}
\begin{itemize} 
  \item Built an Artificial Neural Network (ANN) from scratch to classify handwritten digits (0-9). 
  \item Achieved over 90\% accuracy using Backpropagation algorithm.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Reverse-Polish Calculator}{ - Java, ANTLR, JUnit, OOP Concepts} \hfill \href{https://github.com/Monica20030707/reverse-Polish_calculator}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Applied the Visitor design pattern to traverse ASTs and evaluate expressions, reinforcing compiler theory and object-oriented programming concepts.
  \item Leveraged stacks and tree-based data structures to correctly parse and compute reverse-polish expressions.
  \item Implemented automated unit tests to ensure correctness and reliability of expression evaluation.
\end{itemize}
\end{comment}


\textbf{Traffic Violation Detection System}{ - Javascript, AWS Cloud Services} \hfill \href{https://github.com/Monica20030707/AWS_rekonigition-N-read-database}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Engineered a serverless backend to process license plate images using AWS Rekognition, routing data through SQS and EventBridge for scalable handling.
  \item Implemented Regex-based identification logic to automate fine calculation and notice distribution via automated email workflows.
\end{itemize}

\begin{comment}
\textbf{Network-Wide Ad Blocker (Pi-hole)}{ - Raspberry Pi, Linux, DNS} \hfill \href{https://github.com/Monica20030707}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Engineered a custom network-layer security solution using Linux and Pi-hole to filter DNS traffic across all connected devices.
  \item Enhanced network-wide security and reduced bandwidth consumption by filtering malicious and tracking-heavy domains.
  \item Improved page load speeds by 30\% through proactive ad blocking and DNS caching.
\end{itemize}
\end{comment}

% alternate formatting for projects section
\begin{comment}
% \begin{itemize}
%   \item \textbf{QuantSoftware Toolkit:} Open source Python library for data analysis and machine learning for finance
%   \item \textbf{GitHub Visualization:} Data visualization of Git Log data using D3 to analyze project trends over time
%   \item \textbf{Recommendation System:} Music and movie recommender systems using collaborative filtering on public datasets
%   \item \textbf{Mac Setup:} Book that gives step by step instructions on setting up developer environment on Mac OS
% \end{itemize}
\end{comment}

\vspace{-18.5pt}


% skills section
\section*{Skills}
\textbf{Languages:} Python, Java, JavaScript, TypeScript, SQL, PHP, C++, HTML/CSS, Shell Scripting\\
\textbf{Skills:} Full-stack, RESTful APIs, Agile/Scrum, Unit Testing (Jest, JUnit), CI/CD, AWS Cloud, Gen AI/ML\\
\textbf{Tools:} React, Node.js, Express.js, Docker, AWS Amplify, Git, TensorFlow.js, Redux Toolkit, SQL Server\\

\vspace{-6.5pt}

\end{document}
