\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,            % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[colorlinks=true, linkcolor=black, urlcolor=blue]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering
\usepackage{comment}                % block comment

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=6pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Thuy Nguyen}

\vspace{5pt}

% contact information
\centerline{\href{mailto:thuybohr@gmail.com}{thuybohr@gmail.com} | 206-423-9827 |
\href{https://www.linkedin.com/in/thuy-nguyen-46505121b/}{linkedin.com/in/thuy-nguyen-46505121b}}

\centerline{\href{https://github.com/Monica20030707}{github.com/Monica20030707} | 
\href{https://monica20030707.github.io/}{monica20030707.github.io/}} 

\vspace{-9pt}

% education section
\section*{Education}
\textbf{Bellevue College} -- BS in Computer Science -- 3.6 GPA \hfill September 2021 -- June 2025\\
\vspace{-9pt}
\begin{itemize}
  \item Award: Amazon Scholarship, Activities: Social Media Manager of Computer Science Club
\end{itemize}

\vspace{-18.5pt}

% experience section
\section*{Experience}

\textbf{Sales Specialist,} {Verizon} -- Covington, WA \hfill November 2025 -- Current \\
\vspace{-9pt}
\begin{itemize}
  \item Consistently surpassed monthly sales quotas by achieving 130\% of targets through technical product expertise and consultative solution-selling.
  \item Translated technical specifications into business value for diverse customer segments, helping them navigate complex service and device offerings.
  \item Streamlined inventory workflows and device diagnostic processes, reducing customer wait times and improving store operational efficiency.
\end{itemize}

\textbf{Associate Full Stack Developer,} {Forge Tek Studios} -- Remote \hfill August 2025 -- Current 
\vspace{-9pt}
\begin{itemize}
  \item Built and deployed a production-ready full-stack component-driven React application, integrating external APIs to dynamically render real-time content.
  \item Reduced system load and data ingestion overhead by 80\% through optimization of client-side rendering and synchronization logic.
  \item Designed and deployed a serverless backend to keep costs low and servers flexible for high visitor traffic.
\end{itemize}

\textbf{Teaching Assistant,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- December 2024 \\
\vspace{-9pt}
\begin{itemize}
  \item Guided 40+ students in Java and SQL, adapting communication methods to suit diverse backgrounds and ensuring all learners met course objectives.
  \item Mentored students on software engineering principles like documentation and testing as foundational career skills.
  \item Managed office hours and group labs, fostering a collaborative and learning-oriented environment.
\end{itemize}

\begin{comment}
\textbf{Full Stack Developer Intern,} {METY Technology} -- Remote \hfill September 2024 -- June 2025 
\vspace{-9pt}
\begin{itemize}
  \item Engineered a real-time, interaction-driven application using React and TensorFlow.js (MoveNet), processing live camera input and rendering responsive UI feedback.
  \item Developed secure and scalable RESTful APIs with Express.js and Node.js to manage data flow and backend communication, in frontend, used Tailwind CSS for styling and Redux Toolkits for state managing.
  \item Built and maintained a CI/CD pipeline using AWS Amplify, with automated testing via Jest and code quality enforcement through ESLint.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Open-Source Intern,} {CodeDay} -- Seattle, WA \hfill April 2025 -- May 2025 \\
\vspace{-9pt}
\begin{itemize}
  \item Led team progress as Scrum Master, ensuring timely delivery by coordinating client communications.
  \item Resolved two OED tickets in Agile, through the implementation of database test cases.
  \item Ran and tested the website in various environments with Docker, ensuring its functionality and performance.
\end{itemize}
\end{comment}

\textbf{Coding Competition Developer,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- May 2025 \\
\vspace{-9pt}
\begin{itemize}
  \item Directed onsite technical operations for 30+ participants, ensuring a seamless competition experience and immediate troubleshooting support.
  \item Built a dynamic leaderboard system using PHP and SQL for real-time performance tracking during competitive coding events.
  \item Authored automated test cases across 5 languages to validate participant submissions for algorithm accuracy and efficiency.
\end{itemize}

\begin{comment}
\textbf{Web Design Intern,} {RSVP} -- Sai Gon, Vietnam \hfill July 2022 -- September 2022 \\
\vspace{-9pt}
\begin{itemize}
  \item Designed a Figma mock-up for the company's planned landing page refresh.
  \item Collaborated in a team of 4 developers, handled minor coding tickets and assisted with design works.
  \item Worked closely with clients to ensure our HTML email template suited the clients needs.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Front Desk Assistant} {, Public Safety Department, Bellevue College} -- Bellevue, WA \hfill June 2023 -- August 2023 \\
\vspace{-9pt}
\begin{itemize}
  \item Managed tasks with precision in a fast-paced environment.
  \item Using Canva to design Parking Bookmark for advertising \& assisting users.
  \item Utilized Microsoft Word, Excel and Outlook for efficient data management.
  \item Collaborated with team members to ensure accurate and prompt assistance.
\end{itemize}
\end{comment}

\vspace{-18.5pt}

% projects section
\section*{Projects}

\textbf{Network-Wide Ad Blocker (Pi-hole)}{ - Raspberry Pi, Linux, DNS} \hfill \href{https://github.com/Monica20030707}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Engineered a custom network-layer security solution using Linux and Pi-hole to filter DNS traffic across all connected devices, reducing bandwidth consumption.
  \item Diagnosed and resolved network routing conflicts to ensure zero-latency ad blocking and stable network-wide security.
  \item Improved page load speeds by 30\% through proactive ad blocking and DNS caching.
\end{itemize}

\begin{comment}
\textbf{Stock Ratio Tracker}{ - Python, React, Typescript} \hfill \href{https://github.com/Monica20030707/tradingDashboard-UI}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Architected the data-flow pipeline connecting Python backend calculations to a live React dashboard, ensuring stable, low-latency ratio updates. 
  \item Used JPMorgan Chase’s open-source library called Perspective to generate a live graph that displays a data feed in a clear and visually appealing way for traders to monitor.
  \item Implemented automated unit tests to ensure correctness and reliability.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Read MNIST Handwritten Dataset}{ - Python, Numpy Library} \hfill \href{https://github.com/Monica20030707/Artificial-Neutral-Network_ML}{github.com} \\
\vspace{-9pt}
\begin{itemize} 
  \item Built an Artificial Neural Network (ANN) from scratch to classify handwritten digits (0-9). 
  \item Achieved over 90\% accuracy using Backpropagation algorithm.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Reverse-Polish Calculator}{ - Java, ANTLR, JUnit, OOP Concepts} \hfill \href{https://github.com/Monica20030707/reverse-Polish_calculator}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Applied the Visitor design pattern to traverse ASTs and evaluate expressions, reinforcing compiler theory and object-oriented programming concepts.
  \item Leveraged stacks and tree-based data structures to correctly parse and compute reverse-polish expressions.
  \item Implemented automated unit tests to ensure correctness and reliability of expression evaluation.
\end{itemize}
\end{comment}


\textbf{Traffic Violation Detection System}{ - Javascript, AWS Cloud Services} \hfill \href{https://github.com/Monica20030707/AWS_rekonigition-N-read-database}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Processed license plate images from S3 using AWS Rekognition, sending email notices to offenders with violation details and fines.
  \item Engineered Regex to identify California plates and routed data through SQS and EventBridge for scalable and reliable handling.
\end{itemize}

% alternate formatting for projects section
\begin{comment}
% \begin{itemize}
%   \item \textbf{QuantSoftware Toolkit:} Open source Python library for data analysis and machine learning for finance
%   \item \textbf{GitHub Visualization:} Data visualization of Git Log data using D3 to analyze project trends over time
%   \item \textbf{Recommendation System:} Music and movie recommender systems using collaborative filtering on public datasets
%   \item \textbf{Mac Setup:} Book that gives step by step instructions on setting up developer environment on Mac OS
% \end{itemize}
\end{comment}

\vspace{-18.5pt}


% skills section
\section*{Skills}
\textbf{Languages:} Python, TypeScript, SQL, Java, PHP, JavaScript, Shell Scripting, HTML/CSS\\
\textbf{Skills:} Sales Prospecting, Lead Qualification, Consultative Selling, CRM Management, Technical Communication, Solution Design\\
\textbf{Tools:} CRM (Salesforce/MS Dynamics), Linux, Raspberry Pi, AWS Cloud Services, React, Node.js, Excel, Outlook\\

\vspace{-6.5pt}

\end{document}
