\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,            % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[colorlinks=true, linkcolor=black, urlcolor=blue]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering
\usepackage{comment}                % block comment

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=6pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Thuy Nguyen}

\vspace{5pt}

% contact information
\centerline{\href{mailto:thuybohr@gmail.com}{thuybohr@gmail.com} | 206-423-9827 |
\href{https://www.linkedin.com/in/thuy-nguyen-46505121b/}{linkedin.com/in/thuy-nguyen-46505121b}}

\centerline{\href{https://github.com/Monica20030707}{github.com/Monica20030707} | 
\href{https://monica20030707.github.io/}{monica20030707.github.io/}} 

\vspace{-9pt}

% education section
\section*{Education}
\textbf{Bellevue College} -- BS in Computer Science -- 3.6 GPA \hfill September 2021 -- June 2025\\
\vspace{-9pt}
\begin{itemize}
  \item Award: Amazon Scholarship, Activities: Social Media Manager of Computer Science Club
\end{itemize}

\vspace{-18.5pt}

% experience section
\section*{Experience}

\textbf{Full Stack Developer Intern,} {METY Technology} -- Remote \hfill September 2024 -- June 2025 
\vspace{-9pt}
\begin{itemize}
  \item Engineered a real-time, interaction-driven application using React and TensorFlow.js (MoveNet), processing live camera input to prototype AI-driven UI feedback.
  \item Developed secure and scalable RESTful APIs with Node.js to manage data flow, ensuring reliable communication between AI workloads and frontend components.
  \item Maintained a CI/CD pipeline using AWS Amplify, with automated testing via Jest to ensure the stability and performance of AI integration features.
\end{itemize}

\textbf{Associate Full Stack Developer,} {Forge Tek Studios} -- Remote \hfill August 2025 -- Current 
\vspace{-9pt}
\begin{itemize}
  \item Prototyped and deployed production-ready full-stack components, integrating external APIs to dynamically render real-time content and identify potential automation use cases.
  \item Optimized data synchronization and client-side rendering, focusing on creating stable and maintainable solutions for high-traffic environments.
  \item Managed the full production release lifecycle, including environment configurations and hosting, to deliver functional prototypes used by real customers.
  \item Designed flexible serverless backends to support complex workloads and experimental iterations on new product features.
\end{itemize}

\textbf{Sales Specialist,} {Verizon} -- Covington, WA \hfill November 2025 -- Current \\
\vspace{-9pt}
\begin{itemize}
  \item Explain technical concepts such as bandwidth needs and device compatibility to help stakeholders understand potential technology solutions and outcomes.
  \item Collaborate with team members to resolve technical issues, utilizing diagnostics and hardware verification to ensure accurate data and system performance.
\end{itemize}

\textbf{Teaching Assistant,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- December 2024 \\
\vspace{-9pt}
\begin{itemize}
  \item Guided 40+ students in Java and SQL, creating documentation and learning materials to help individuals confidently explore and use technical tools.
  \item Educated students in relational database design and data validation techniques, enhancing assignment quality and problem-solving skills by 20\%.
\end{itemize}

\begin{comment}
\textbf{Open-Source Intern,} {CodeDay} -- Seattle, WA \hfill April 2025 -- May 2025 \\
\vspace{-9pt}
\begin{itemize}
  \item Led team progress as Scrum Master, ensuring timely delivery by coordinating client communications.
  \item Resolved two OED tickets in Agile, through the implementation of database test cases.
  \item Ran and tested the website in various environments with Docker, ensuring its functionality and performance.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Coding Competition Developer,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- May 2025 \\
\vspace{-9pt}
\begin{itemize}
  \item Developed real-time score updates using SQL and PHP, increasing efficiency by 40\%.
  \item Enhanced web interfaces with HTML and CSS, boosting user satisfaction by 30\%.
  \item Created coding problems with auto test cases for Java, Python, C++, and Golang.
  \item Assisted onsite at a competition with 30+ participants to ensure smooth operations.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Web Design Intern,} {RSVP} -- Sai Gon, Vietnam \hfill July 2022 -- September 2022 \\
\vspace{-9pt}
\begin{itemize}
  \item Designed a Figma mock-up for the company's planned landing page refresh.
  \item Collaborated in a team of 4 developers, handled minor coding tickets and assisted with design works.
  \item Worked closely with clients to ensure our HTML email template suited the clients needs.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Front Desk Assistant} {, Public Safety Department, Bellevue College} -- Bellevue, WA \hfill June 2023 -- August 2023 \\
\vspace{-9pt}
\begin{itemize}
  \item Managed tasks with precision in a fast-paced environment.
  \item Using Canva to design Parking Bookmark for advertising \& assisting users.
  \item Utilized Microsoft Word, Excel and Outlook for efficient data management.
  \item Collaborated with team members to ensure accurate and prompt assistance.
\end{itemize}
\end{comment}

\vspace{-18.5pt}

% projects section
\section*{Projects}

\textbf{Read MNIST Handwritten Dataset}{ - Python, Numpy Library} \hfill \href{https://github.com/Monica20030707/Artificial-Neutral-Network_ML}{github.com} \\
\vspace{-9pt}
\begin{itemize} 
  \item Built an Artificial Neural Network (ANN) from scratch to classify handwritten digits, demonstrating core AI concepts, backpropagation, and data preparation. 
  \item Achieved over 90\% accuracy through iterative experimentation and model validation.
\end{itemize}

\textbf{Traffic Violation Detection System}{ - Javascript, AWS Cloud Services} \hfill \href{https://github.com/Monica20030707/AWS_rekonigition-N-read-database}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Prototyped a cloud-based solution using AWS Rekognition to automate detection workloads, following event-driven architecture patterns.
  \item Engineered license plate identification and notification workflows, managing data flow through SQS and EventBridge for reliable outcome tracking.
\end{itemize}

\begin{comment}
\textbf{Stock Ratio Tracker}{ - Python, React, Typescript} \hfill \href{https://github.com/Monica20030707/tradingDashboard-UI}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Architected the data-flow pipeline connecting Python backend calculations to a live React dashboard, ensuring stable, low-latency ratio updates. 
  \item Used JPMorgan Chase’s open-source library called Perspective to generate a live graph that displays a data feed in a clear and visually appealing way for traders to monitor.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Reverse-Polish Calculator}{ - Java, ANTLR, JUnit, OOP Concepts} \hfill \href{https://github.com/Monica20030707/reverse-Polish_calculator}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Applied the Visitor design pattern to traverse ASTs and evaluate expressions, reinforcing compiler theory and object-oriented programming concepts.
  \item Leveraged stacks and tree-based data structures to correctly parse and compute reverse-polish expressions.
  \item Implemented automated unit tests to ensure correctness and reliability of expression evaluation.
\end{itemize}
\end{comment}


\vspace{-18.5pt}


% skills section
\section*{Skills}
\textbf{Languages:} Python, JavaScript, TypeScript, Java, Go, SQL, MySQL, Kotlin, C++\\
\textbf{Skills:} AI/ML Prototyping, TensorFlow.js, Data Validation, API Design, Cloud Concepts, Documentation\\
\textbf{Tools:} Microsoft Azure (Basics), AWS Cloud Services, React, Node.js, Docker, Git, Jira\\

\vspace{-6.5pt}

\end{document}