\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,            % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[colorlinks=true, linkcolor=black, urlcolor=blue]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering
\usepackage{comment}                % block comment

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=6pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Thuy Nguyen}

\vspace{5pt}

% contact information
\centerline{\href{mailto:thuybohr@gmail.com}{thuybohr@gmail.com} | 206-423-9827 |
\href{https://www.linkedin.com/in/thuy-nguyen-46505121b/}{linkedin.com/in/thuy-nguyen-46505121b}}

\centerline{\href{https://github.com/Monica20030707}{github.com/Monica20030707} | 
\href{https://monica20030707.github.io/}{monica20030707.github.io/}} 

\vspace{-9pt}

% education section
\section*{Education}
\textbf{Bellevue College} -- BS in Computer Science -- 3.6 GPA \hfill September 2021 -- June 2025\\
\vspace{-9pt}
\begin{itemize}
  \item Award: Amazon Scholarship, Activities: Social Media Manager of Computer Science Club
\end{itemize}

\vspace{-18.5pt}

% experience section
\section*{Experience}

\textbf{Sales Specialist,} {Verizon} -- Covington, WA \hfill November 2025 -- Current \\
\vspace{-9pt}
\begin{itemize}
  \item De-escalated complex technical issues by explaining bandwidth optimization, signal propagation, and network topology to non-technical customers to drive informed decision-making.
  \item Consistently surpassed monthly sales quotas by achieving 130\% of targets through technical product expertise and consultative solution-selling.
  \item Developed ongoing relationships with strategic business partners by identifying their long-term growth potential and tailoring technical solutions to their specific needs.
\end{itemize}

\textbf{Associate Full Stack Developer,} {Forge Tek Studios} -- Remote \hfill August 2025 -- Current 
\vspace{-9pt}
\begin{itemize}
  \item Architected a modular React frontend with a serverless backend, leveraging custom hooks and context for efficient state management and dynamic data fetching.
  \item Implemented dynamic data fetching and caching strategies for third-party APIs to reduce latency and improve system responsiveness for high visitor traffic.
  \item Managed the end-to-end development and deployment lifecycle, ensuring high standards for code quality and performance in a production environment.
\end{itemize}

\textbf{Full Stack Developer Intern,} {METY Technology} -- Remote \hfill September 2024 -- June 2025 
\vspace{-9pt}
\begin{itemize}
  \item Integrated real-time machine learning models (MoveNet) with React using TensorFlow.js to enable low-latency, gesture-based user interaction directly in the browser.
  \item Developed secure and scalable RESTful APIs with Express.js and Node.js to manage data flow and backend communication for interaction-driven applications.
  \item Built and maintained a CI/CD pipeline using AWS Amplify, with automated testing via Jest to ensure consistent delivery and quality standards.
\end{itemize}

\begin{comment}
\textbf{Teaching Assistant,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- December 2024 \\
\vspace{-9pt}
\begin{itemize}
  \item Guided 40+ students in Java and SQL, with class materials during and after class.
  \item Educated students in relational database design and MySQL Workbench operations.
  \item Elevated student proficiency in JUnit and Javadoc, enhancing assignment quality by 20\%.
\end{itemize}
\end{comment}

\vspace{-18.5pt}

% projects section
\section*{Projects}

\textbf{MNIST Handwritten Digit Classifier}{ - Python, NumPy} \hfill \href{https://github.com/Monica20030707/Artificial-Neutral-Network_ML}{github.com} \\
\vspace{-9pt}
\begin{itemize} 
  \item Engineered a multi-layer perceptron architecture from scratch, implementing forward and backward propagation using NumPy vectorization for high computational efficiency. 
  \item Attained 90\%+ classification accuracy on the standard MNIST benchmark, demonstrating a deep understanding of mathematical machine learning foundations.
\end{itemize}

\textbf{Traffic Violation Detection System}{ - JavaScript, AWS Rekognition, S3, SQS} \hfill \href{https://github.com/Monica20030707/AWS_rekonigition-N-read-database}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Architected an event-driven serverless pipeline on AWS, integrating Rekognition for automated image analysis and SQS for decoupled message processing.
  \item Automated the violation detection and notification workflow, reducing manual processing time by over 90\% through efficient cloud resource management.
\end{itemize}

\vspace{-18.5pt}

% skills section
\section*{Skills}
\textbf{Languages:} Python, C++, Java, JavaScript, TypeScript, SQL, HTML, CSS\\
\textbf{Skills:} Machine Learning (TensorFlow.js, NumPy), Data Pipelines, RESTful APIs, Technical Pre-sales, Embedded ML Concepts\\
\textbf{Tools:} AWS (Rekognition, S3, SQS, Amplify), React, Node.js, Git, Docker, Linux, CI/CD\\

\vspace{-6.5pt}

\end{document}
