\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,            % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[colorlinks=true, linkcolor=black, urlcolor=blue]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering
\usepackage{comment}                % block comment

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=6pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Thuy Nguyen}

\vspace{5pt}

% contact information
\centerline{\href{mailto:thuybohr@gmail.com}{thuybohr@gmail.com} | 206-423-9827 |
\href{https://www.linkedin.com/in/thuy-nguyen-46505121b/}{linkedin.com/in/thuy-nguyen-46505121b}}

\centerline{\href{https://github.com/Monica20030707}{github.com/Monica20030707} | 
\href{https://monica20030707.github.io/}{monica20030707.github.io/}} 

\vspace{-9pt}

% education section
\section*{Education}
\textbf{Bellevue College} -- BS in Computer Science -- 3.6 GPA \hfill September 2021 -- June 2025\\
\vspace{-9pt}
\begin{itemize}
  \item Award: Amazon Scholarship, Activities: Social Media Manager of Computer Science Club
\end{itemize}

\vspace{-18.5pt}

% experience section
\section*{Experience}

\textbf{Sales Specialist,} {Verizon} -- Covington, WA \hfill November 2025 -- Current \\
\vspace{-9pt}
\begin{itemize}
  \item Consistently surpassed monthly sales quotas by achieving 130\% of targets through technical product expertise and consultative solution-selling for SMB and consumer segments.
  \item Contributed to regional sales targets by translating complex technical specifications into actionable business value, driving customer acquisition and retention.
  \item Streamlined inventory workflows and device diagnostic processes, reducing customer wait times and improving store operational efficiency.
\end{itemize}

\textbf{Open-Source Intern (Scrum Master),} {CodeDay} -- Seattle, WA \hfill April 2025 -- May 2025 \\
\vspace{-9pt}
\begin{itemize}
  \item Drove project velocity as Scrum Master, meeting all client deadlines through proactive blocker removal and cross-functional communication with stakeholders.
  \item Facilitated daily stand-ups and retrospectives, aligning a distributed team on weekly sprint goals and deliverable timelines in an Agile environment.
  \item Collaborated directly with stakeholders to clarify software requirements and translate them into actionable development tasks.
\end{itemize}

\textbf{Associate Full Stack Developer,} {Forge Tek Studios} -- Remote \hfill August 2025 -- Current 
\vspace{-9pt}
\begin{itemize}
  \item Built and deployed a production-ready full-stack application, gaining deep technical insight into SaaS architecture and API integration.
  \item Reduced system load and ingestion overhead by 80\% through optimization of client-side rendering, ensuring a high-performance experience for end-users.
  \item Owned the end-to-end development lifecycle, ensuring high standards for code quality and performance-sensitive UI updates.
\end{itemize}

\textbf{Teaching Assistant,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- December 2024 \\
\vspace{-9pt}
\begin{itemize}
  \item Provided in-depth technical coaching and guidance to 40+ students, demonstrating strong communication skills and a growth-oriented mindset.
  \item Improved student success rates by 20\% through targeted feedback and supplemental instruction in technical best practices.
  \item Managed office hours and group labs, adapting communication styles to suit diverse backgrounds and learning speeds.
\end{itemize}

\begin{comment}
\textbf{Front Desk Assistant} {, Public Safety Department, Bellevue College} -- Bellevue, WA \hfill June 2023 -- August 2023 \\
\vspace{-9pt}
\begin{itemize}
  \item Managed administrative workflows with precision in a high-volume, fast-paced environment.
  \item Utilized Microsoft Excel and Outlook for efficient data management and appointment scheduling.
\end{itemize}
\end{comment}

\vspace{-18.5pt}

% projects section
\section*{Projects}

\textbf{Stock Ratio Tracker}{ - Python, React, Typescript} \hfill \href{https://github.com/Monica20030707/tradingDashboard-UI}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Architected a real-time data-flow pipeline connecting financial metrics to a live dashboard, focusing on providing business owners with clear, actionable data. 
  \item Evaluated and selected industry-standard visualization tools to deliver a production-quality user experience.
\end{itemize}

\textbf{Traffic Violation Detection System}{ - Javascript, AWS Cloud Services} \hfill \href{https://github.com/Monica20030707/AWS_rekonigition-N-read-database}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Engineered an automated serverless pipeline on AWS, demonstrating an understanding of how automation tools can simplify complex manual processes.
  \item Reduced manual processing time by 90\% through event-driven architecture and automated notice generation.
\end{itemize}

\vspace{-18.5pt}

% skills section
\section*{Skills}
\textbf{Languages:} SQL (MySQL), Python, JavaScript, TypeScript, Java, C++, HTML/CSS, Shell Scripting\\
\textbf{Skills:} Outbound Sales, Pipeline Generation, Consultative Selling, SaaS Acumen, Agile/Scrum, SMB Relations\\
\textbf{Tools:} CRM (Salesforce), Microsoft Excel, Microsoft Outlook, G-Suite, AWS, Docker, React, Node.js\\

\vspace{-6.5pt}

\end{document}
