\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,            % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[colorlinks=true, linkcolor=black, urlcolor=blue]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering
\usepackage{comment}                % block comment

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=6pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Thuy Nguyen}

\vspace{5pt}

% contact information
\centerline{\href{mailto:thuybohr@gmail.com}{thuybohr@gmail.com} | 206-423-9827 |
\href{https://www.linkedin.com/in/thuy-nguyen-46505121b/}{linkedin.com/in/thuy-nguyen-46505121b}}

\centerline{\href{https://github.com/Monica20030707}{github.com/Monica20030707} | 
\href{https://monica20030707.github.io/}{monica20030707.github.io/}} 

\vspace{-9pt}

% education section
\section*{Education}
\textbf{Bellevue College} -- BS in Computer Science -- 3.6 GPA \hfill September 2021 -- June 2025\\
\vspace{-9pt}
\begin{itemize}
  \item Award: Amazon Scholarship, Activities: Social Media Manager of Computer Science Club
\end{itemize}

\vspace{-18.5pt}

% experience section
\section*{Experience}

\textbf{Sales Specialist,} {Verizon} -- Covington, WA \hfill November 2025 -- Current \\
\vspace{-9pt}
\begin{itemize}
  \item Consistently surpassed monthly sales quotas by achieving 130\% of targets through technical product expertise and consultative solution-selling.
  \item De-escalated complex technical issues by explaining network topology, bandwidth optimization, and signal propagation to customers, serving as their primary technical advisor.
  \item Conducted hardware diagnostics and firmware validation on mobile devices and networking equipment to ensure optimal performance and security readiness.
\end{itemize}

\textbf{Associate Full Stack Developer,} {Forge Tek Studios} -- Remote \hfill August 2025 -- Current 
\vspace{-9pt}
\begin{itemize}
  \item Built and deployed production-ready SaaS-style React applications, integrating external APIs to dynamically render real-time content while maintaining high availability.
  \item Optimized client-side rendering and data synchronization, reducing ingestion overhead by 80\%—focusing on performance-sensitive UI updates and data integrity.
  \item Delivered a production-ready application that handled high traffic volumes with minimal infrastructure costs using serverless technologies on cloud platforms.
\end{itemize}

\textbf{Teaching Assistant,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- December 2024 \\
\vspace{-9pt}
\begin{itemize}
  \item Provided technical coaching on relational schema design, query optimization, and Java unit testing patterns to a classroom of 40+ students.
  \item Mentored students on software engineering principles like documentation and testing (JUnit) as foundational practices for building stable and secure platforms.
  \item Facilitated workshops on MySQL Workbench for database visualization, helping students articulate complex technical concepts in structured presentations.
\end{itemize}

\vspace{-18.5pt}

% projects section
\section*{Projects}

\textbf{Automated Document Generation Pipeline}{ - Python, YAML, GitHub Actions} \hfill \href{https://github.com/Monica20030707/Tex_OrangeLeaf-mcp}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Architected an automated pipeline using Python and YAML to dynamically tailor technical documentation based on targeted requirement analysis.
  \item Reduced manual tailoring time by 90\% by automating the data selection and document formatting process through an LLM-driven orchestration engine.
  \item Engineered automated CI/CD workflows with GitHub Actions to ensure consistent, environment-independent builds and artifact management.
\end{itemize}

\textbf{Traffic Violation Detection System}{ - AWS, JavaScript, Event-Driven Architecture} \hfill \href{https://github.com/Monica20030707/AWS_rekonigition-N-read-database}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Architected an event-driven serverless pipeline on AWS, integrating Rekognition for image analysis and SQS for decoupled, resilient message processing.
  \item Implemented pattern matching with Regex to filter and route geographic plate data, triggering automated SES-based notification workflows.
  \item Leveraged S3, EventBridge, and Lambda to build a scalable, cost-efficient solution for real-time data ingestion and analysis.
\end{itemize}

\vspace{-18.5pt}


% skills section
\section*{Skills}
\textbf{Languages:} Python, Java, JavaScript, SQL (MySQL), PowerShell, Bash, TypeScript, LaTeX, YAML, HTML/CSS\\
\textbf{Skills:} Pre-sales Engineering, Cloud Architecture (AWS), Data Security, SaaS Integration, CI/CD, Technical Support\\
\textbf{Tools:} Microsoft 365, Salesforce, Windows/macOS/Linux, GitHub Actions, Docker, React, Node.js, AWS SQS/S3\\

\vspace{-6.5pt}

\end{document}
