\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,            % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[colorlinks=true, linkcolor=black, urlcolor=blue]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering
\usepackage{comment}                % block comment

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=6pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Thuy Nguyen}

\vspace{5pt}

% contact information
\centerline{\href{mailto:thuybohr@gmail.com}{thuybohr@gmail.com} | 206-423-9827 |
\href{https://www.linkedin.com/in/thuy-nguyen-46505121b/}{linkedin.com/in/thuy-nguyen-46505121b}}

\centerline{\href{https://github.com/Monica20030707}{github.com/Monica20030707} | 
\href{https://monica20030707.github.io/}{monica20030707.github.io/}} 

\vspace{-9pt}

% education section
\section*{Education}
\textbf{Bellevue College} -- BS in Computer Science -- 3.6 GPA \hfill September 2021 -- June 2025\\
\vspace{-9pt}
\begin{itemize}
  \item Award: Amazon Scholarship, Activities: Social Media Manager of Computer Science Club
\end{itemize}

\vspace{-18.5pt}

% experience section
\section*{Experience}

\textbf{Sales Specialist,} {Verizon} -- Covington, WA \hfill November 2025 -- Current \\
\vspace{-9pt}
\begin{itemize}
  \item De-escalated complex technical issues by explaining bandwidth optimization, signal propagation, and network topology to non-technical customers, ensuring world-class support.
  \item Conducted hardware diagnostics and firmware validation on mobile devices and networking equipment to identify and mitigate technical concerns.
  \item Consistently surpassed monthly targets by achieving 130\% of goals through technical product expertise and consultative problem-solving.
\end{itemize}

\textbf{Associate Full Stack Developer,} {Forge Tek Studios} -- Remote \hfill August 2025 -- Current 
\vspace{-9pt}
\begin{itemize}
  \item Architected a modular React frontend with a serverless backend, leveraging custom hooks and context for efficient state management and data analysis.
  \item Built and deployed production-ready applications, integrating third-party APIs to dynamically render real-time content while maintaining high availability and security.
  \item Owned the end-to-end development lifecycle, advocating for scalable solutions to meet customer requirements and performance standards.
\end{itemize}

\textbf{Teaching Assistant,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- December 2024 \\
\vspace{-9pt}
\begin{itemize}
  \item Provided in-depth technical coaching on Java, SQL, and relational schema design to a classroom of 40+ students, adapting methods to suit diverse backgrounds.
  \item Facilitated workshops on MySQL Workbench for database visualization and management, improving student success rates by 20\%.
  \item Mentored students on software engineering principles like documentation and unit testing as foundational skills for building stable and secure platforms.
\end{itemize}

\vspace{-18.5pt}

% projects section
\section*{Projects}

\textbf{Automated Document Generation Pipeline}{ - Python, YAML, GitHub Actions} \hfill \href{https://github.com/Monica20030707/Tex_OrangeLeaf-mcp}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Developed an automated pipeline that programmatically generates tailored technical documentation from a versioned YAML data store using LLM-driven content selection.
  \item Reduced manual processing time by 90\% by automating data selection and document formatting through an orchestration engine and CI/CD workflows.
  \item Engineered automated workflows with GitHub Actions to ensure consistent, environment-independent builds and artifact management.
\end{itemize}

\textbf{Traffic Violation Detection System}{ - AWS, JavaScript, Event-Driven Architecture} \hfill \href{https://github.com/Monica20030707/AWS_rekonigition-N-read-database}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Architected an event-driven serverless pipeline on AWS, integrating Rekognition for image analysis and SQS for decoupled, resilient message processing.
  \item Implemented pattern matching with Regex to filter geographic data and trigger automated notification workflows via EventBridge and SES.
  \item Leveraged S3 and Lambda to build a scalable solution for real-time data ingestion and analysis, reducing system load and operational costs.
\end{itemize}

\vspace{-18.5pt}


% skills section
\section*{Skills}
\textbf{Languages:} Java, SQL (MySQL), Python, JavaScript, TypeScript, PowerShell, Bash, C++, PHP, LaTeX, YAML\\
\textbf{Skills:} Technical Support, Problem Solving, Full-stack, Data Analytics, Systems Administration, CI/CD, RDBMS\\
\textbf{Tools:} Linux, Windows, AWS, React, Node.js, GitHub Actions, Docker, MySQL Workbench, CRM\\

\vspace{-6.5pt}

\end{document}
