\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,            % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[colorlinks=true, linkcolor=black, urlcolor=blue]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering
\usepackage{comment}                % block comment

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=6pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Thuy Nguyen}

\vspace{5pt}

% contact information
\centerline{\href{mailto:thuybohr@gmail.com}{thuybohr@gmail.com} | 206-423-9827 |
\href{https://www.linkedin.com/in/thuy-nguyen-46505121b/}{linkedin.com/in/thuy-nguyen-46505121b}}

\centerline{\href{https://github.com/Monica20030707}{github.com/Monica20030707} | 
\href{https://monica20030707.github.io/}{monica20030707.github.io/}} 

\vspace{-9pt}

% education section
\section*{Education}
\textbf{Bellevue College} -- BS in Computer Science -- 3.6 GPA \hfill September 2021 -- June 2025\\
\vspace{-9pt}
\begin{itemize}
  \item Award: Amazon Scholarship, Activities: Social Media Manager of Computer Science Club
\end{itemize}

\vspace{-18.5pt}

% experience section
\section*{Experience}

\textbf{Sales Specialist,} {Verizon} -- Covington, WA \hfill November 2025 -- Current \\
\vspace{-9pt}
\begin{itemize}
  \item Solicit business requirements and explain technical concepts like signal strength and device compatibility to develop technical sales strategies for varied customer needs.
  \item Successfully demonstrate solutions by configuring devices and running diagnostics, acting as a trusted advisor to help customers make informed, value-driven decisions.
\end{itemize}

\textbf{Associate Full Stack Developer,} {Forge Tek Studios} -- Remote \hfill August 2025 -- Current 
\vspace{-9pt}
\begin{itemize}
  \item Execute rapid prototyping and deployment of a production-ready React application, integrating external APIs to bring connected customer experiences to life.
  \item Optimize data synchronization and client-side rendering, reducing load overhead by 80\%, focusing on delivering stable and maintainable solutions for real users.
  \item Manage the full production release lifecycle, ensuring environment configurations and hosting deliver reliable business value for high visitor traffic.
  \item Designed a serverless backend to maintain flexibility and scalability, aligning innovative technical strategy with client performance needs.
\end{itemize}

\textbf{Full Stack Developer Intern,} {METY Technology} -- Remote \hfill September 2024 -- June 2025 
\vspace{-9pt}
\begin{itemize}
  \item Engineered an interaction-driven application using React and TensorFlow.js, demonstrating how connected experiences come to life through live technical walkthroughs.
  \item Developed secure RESTful APIs with Node.js to manage complex data flow, collaborating with internal teams to align technology solutions with business objectives.
  \item Maintained a CI/CD pipeline using AWS Amplify, with automated testing via Jest to validate solution reliability and performance in a fast-paced environment.
\end{itemize}

\textbf{Open-Source Intern,} {CodeDay} -- Seattle, WA \hfill April 2025 -- May 2025 \\
\vspace{-9pt}
\begin{itemize}
  \item Led team progress as Scrum Master, orchestrating cross-functional coordination and client communications to drive consensus on solution delivery.
  \item Resolved complex database tickets in an Agile environment, using research and business assessment capabilities to define and solve sophisticated technical problems.
  \item Ran and tested web applications in Docker across various environments, ensuring stable functionality and high-quality solutioning for a global community.
\end{itemize}

\begin{comment}
\textbf{Teaching Assistant,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- December 2024 \\
\vspace{-9pt}
\begin{itemize}
  \item Guided 40+ students in Java and SQL, with class materials during and after class.
  \item Educated students in relational database design and MySQL Workbench operations.
  \item Elevated student proficiency in JUnit and Javadoc, enhancing assignment quality by 20\%.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Coding Competition Developer,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- May 2025 \\
\vspace{-9pt}
\begin{itemize}
  \item Developed real-time score updates using SQL and PHP, increasing efficiency by 40\%.
  \item Enhanced web interfaces with HTML and CSS, boosting user satisfaction by 30\%.
  \item Created coding problems with auto test cases for Java, Python, C++, and Golang.
  \item Assisted onsite at a competition with 30+ participants to ensure smooth operations.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Web Design Intern,} {RSVP} -- Sai Gon, Vietnam \hfill July 2022 -- September 2022 \\
\vspace{-9pt}
\begin{itemize}
  \item Designed a Figma mock-up for the company's planned landing page refresh.
  \item Collaborated in a team of 4 developers, handled minor coding tickets and assisted with design works.
  \item Worked closely with clients to ensure our HTML email template suited the clients needs.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Front Desk Assistant} {, Public Safety Department, Bellevue College} -- Bellevue, WA \hfill June 2023 -- August 2023 \\
\vspace{-9pt}
\begin{itemize}
  \item Managed tasks with precision in a fast-paced environment.
  \item Using Canva to design Parking Bookmark for advertising \& assisting users.
  \item Utilized Microsoft Word, Excel and Outlook for efficient data management.
  \item Collaborated with team members to ensure accurate and prompt assistance.
\end{itemize}
\end{comment}

\vspace{-18.5pt}

% projects section
\section*{Projects}

\textbf{Stock Ratio Tracker}{ - Python, React, Typescript} \hfill \href{https://github.com/Monica20030707/tradingDashboard-UI}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Architected a data-flow pipeline connecting Python backend calculations to a live React dashboard, acting as a rapid prototype to show a path to value for traders. 
  \item Used open-source visualization libraries to generate a live graph, demonstrating the connected experience of real-time data monitoring and business strategy.
\end{itemize}

\begin{comment}
\textbf{Read MNIST Handwritten Dataset}{ - Python, Numpy Library} \hfill \href{https://github.com/Monica20030707/Artificial-Neutral-Network_ML}{github.com} \\
\vspace{-9pt}
\begin{itemize} 
  \item Built an Artificial Neural Network (ANN) from scratch to classify handwritten digits (0-9). 
  \item Achieved over 90\% accuracy using Backpropagation algorithm.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Reverse-Polish Calculator}{ - Java, ANTLR, JUnit, OOP Concepts} \hfill \href{https://github.com/Monica20030707/reverse-Polish_calculator}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Applied the Visitor design pattern to traverse ASTs and evaluate expressions, reinforcing compiler theory and object-oriented programming concepts.
  \item Leveraged stacks and tree-based data structures to correctly parse and compute reverse-polish expressions.
  \item Implemented automated unit tests to ensure correctness and reliability of expression evaluation.
\end{itemize}
\end{comment}


\textbf{Traffic Violation Detection System}{ - Javascript, AWS Cloud Services} \hfill \href{https://github.com/Monica20030707/AWS_rekonigition-N-read-database}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Designed an event-driven strategy using AWS Cloud Services to automate compliance detection, solving sophisticated business problems through technical innovation.
  \item Engineered license plate identification workflows routed through SQS and EventBridge, aligning customer journey strategies with long-term IT roadmaps.
\end{itemize}

\vspace{-18.5pt}

% skills section
\section*{Skills}
\textbf{Languages:} Python, Go, TypeScript, Java, MySQL, JavaScript, HTML/CSS, SQL, Next.js, Kotlin\\
\textbf{Skills:} Rapid Prototyping, Technical Sales Strategy, Solutioning, Cross-functional Collaboration, Relational Databases, Agile\\
\textbf{Tools:} AWS Cloud Services (S3, SQS, EventBridge), React, Node.js, Docker, Kubernetes, Jira, Git\\

\vspace{-6.5pt}

\end{document}