\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,            % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[colorlinks=true, linkcolor=black, urlcolor=blue]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering
\usepackage{comment}                % block comment

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=6pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Thuy Nguyen}

\vspace{5pt}

% contact information
\centerline{\href{mailto:thuybohr@gmail.com}{thuybohr@gmail.com} | 206-423-9827 |
\href{https://www.linkedin.com/in/thuy-nguyen-46505121b/}{linkedin.com/in/thuy-nguyen-46505121b}}

\centerline{\href{https://github.com/Monica20030707}{github.com/Monica20030707} | 
\href{https://monica20030707.github.io/}{monica20030707.github.io/}} 

\vspace{-9pt}

% education section
\section*{Education}
\textbf{Bellevue College} -- BS in Computer Science -- 3.6 GPA \hfill September 2021 -- June 2025\\
\vspace{-9pt}
\begin{itemize}
  \item Award: Amazon Scholarship, Activities: Social Media Manager of Computer Science Club
\end{itemize}

\vspace{-18.5pt}

% experience section
\section*{Experience}

\textbf{Sales Specialist,} {Verizon} -- Covington, WA \hfill November 2025 -- Current \\
\vspace{-9pt}
\begin{itemize}
  \item Explain complex technical concepts, such as bandwidth optimization and network topology, to diverse customer segments to facilitate informed purchasing decisions.
  \item Consistently surpass monthly sales quotas by achieving 130\% of targets through technical product expertise and consultative solution-selling.
  \item Support regional sales operations by identifying and initiating partnerships with strategic business clients, serving as their primary technical point of contact.
\end{itemize}

\textbf{Associate Full Stack Developer,} {Forge Tek Studios} -- Remote \hfill August 2025 -- Current 
\vspace{-9pt}
\begin{itemize}
  \item Managed the full production release lifecycle of a React application, coordinating between technical stakeholders and external API providers like Steam and Fab Marketplace.
  \item Optimized data synchronization and system performance, reducing load overhead by 80\% through careful analysis of UI updates and backend data modeling.
  \item Designed a serverless backend to handle high traffic volumes efficiently, ensuring project deliverables met scalability and cost-compliance requirements.
\end{itemize}

\textbf{Teaching Assistant,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- December 2024 \\
\vspace{-9pt}
\begin{itemize}
  \item Mentored 40+ students on software engineering principles, including technical documentation (Javadoc) and rigorous testing (JUnit) as foundational project skills.
  \item Facilitated workshops on relational database design and MySQL Workbench, translating abstract engineering concepts into actionable student projects.
  \item Improved assignment quality by 20\% through targeted technical feedback and clear communication of project requirements and milestones.
\end{itemize}

\begin{comment}
\textbf{Full Stack Developer Intern,} {METY Technology} -- Remote \hfill September 2024 -- June 2025 
\vspace{-9pt}
\begin{itemize}
  \item Engineered a real-time, interaction-driven application using React and TensorFlow.js (MoveNet), processing live camera input and rendering responsive UI feedback.
  \item Developed secure and scalable RESTful APIs with Express.js and Node.js to manage data flow and backend communication, in frontend, used Tailwind CSS for styling and Redux Toolkits for state managing.
  \item Built and maintained a CI/CD pipeline using AWS Amplify, with automated testing via Jest and code quality enforcement through ESLint.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Open-Source Intern,} {CodeDay} -- Seattle, WA \hfill April 2025 -- May 2025 \\
\vspace{-9pt}
\begin{itemize}
  \item Led team progress as Scrum Master, ensuring timely delivery by coordinating client communications.
  \item Resolved two OED tickets in Agile, through the implementation of database test cases.
  \item Ran and tested the website in various environments with Docker, ensuring its functionality and performance.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Coding Competition Developer,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- May 2025 \\
\vspace{-9pt}
\begin{itemize}
  \item Developed real-time score updates using SQL and PHP, increasing efficiency by 40\%.
  \item Enhanced web interfaces with HTML and CSS, boosting user satisfaction by 30\%.
  \item Created coding problems with auto test cases for Java, Python, C++, and Golang.
  \item Assisted onsite at a competition with 30+ participants to ensure smooth operations.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Web Design Intern,} {RSVP} -- Sai Gon, Vietnam \hfill July 2022 -- September 2022 \\
\vspace{-9pt}
\begin{itemize}
  \item Designed a Figma mock-up for the company's planned landing page refresh.
  \item Collaborated in a team of 4 developers, handled minor coding tickets and assisted with design works.
  \item Worked closely with clients to ensure our HTML email template suited the clients needs.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Front Desk Assistant} {, Public Safety Department, Bellevue College} -- Bellevue, WA \hfill June 2023 -- August 2023 \\
\vspace{-9pt}
\begin{itemize}
  \item Managed tasks with precision in a fast-paced environment.
  \item Using Canva to design Parking Bookmark for advertising \& assisting users.
  \item Utilized Microsoft Word, Excel and Outlook for efficient data management.
  \item Collaborated with team members to ensure accurate and prompt assistance.
\end{itemize}
\end{comment}

\vspace{-18.5pt}

% projects section
\section*{Projects}

\textbf{Stock Ratio Tracker}{ - Python, React, Typescript} \hfill \href{https://github.com/Monica20030707/tradingDashboard-UI}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Architected a data-flow pipeline connecting backend calculations to a live dashboard, ensuring stable, low-latency updates for real-time monitoring.
  \item Leveraged high-performance streaming libraries to reduce visualization latency, increasing decision-making efficiency by 40\% through intuitive interface design.
\end{itemize}

\textbf{Traffic Violation Detection System}{ - JavaScript, AWS Cloud Services} \hfill \href{https://github.com/Monica20030707/AWS_rekonigition-N-read-database}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Engineered an automated violation notification workflow using AWS Rekognition and event-driven architecture, reducing manual processing time by over 90\%.
  \item Implemented pattern-matching logic to filter geographic data and route event-driven alerts, ensuring accurate handling of project-specific contract requirements.
\end{itemize}

\begin{comment}
\textbf{Read MNIST Handwritten Dataset}{ - Python, Numpy Library} \hfill \href{https://github.com/Monica20030707/Artificial-Neutral-Network_ML}{github.com} \\
\vspace{-9pt}
\begin{itemize} 
  \item Built an Artificial Neural Network (ANN) from scratch to classify handwritten digits (0-9). 
  \item Achieved over 90\% accuracy using Backpropagation algorithm.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Reverse-Polish Calculator}{ - Java, ANTLR, JUnit, OOP Concepts} \hfill \href{https://github.com/Monica20030707/reverse-Polish_calculator}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Applied the Visitor design pattern to traverse ASTs and evaluate expressions, reinforcing compiler theory and object-oriented programming concepts.
  \item Leveraged stacks and tree-based data structures to correctly parse and compute reverse-polish expressions.
  \item Implemented automated unit tests to ensure correctness and reliability of expression evaluation.
\end{itemize}
\end{comment}

\vspace{-18.5pt}

% skills section
\section*{Skills}
\textbf{Languages:} Python, SQL (MySQL), Java, JavaScript, TypeScript, C++, HTML/CSS, Go\\
\textbf{Skills:} Technical Documentation, Proposal Support, Solution Selling, Data Modeling, Project Lifecycle Management\\
\textbf{Tools:} Microsoft Office (Excel, Word, PowerPoint), AWS, React, Node.js, Git, Docker, Javadoc, JUnit\\

\vspace{-6.5pt}

\end{document}
