\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,            % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[colorlinks=true, linkcolor=black, urlcolor=blue]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering
\usepackage{comment}                % block comment

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=6pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Thuy Nguyen}

\vspace{5pt}

% contact information
\centerline{\href{mailto:thuybohr@gmail.com}{thuybohr@gmail.com} | 206-423-9827 |
\href{https://www.linkedin.com/in/thuy-nguyen-46505121b/}{linkedin.com/in/thuy-nguyen-46505121b}}

\centerline{\href{https://github.com/Monica20030707}{github.com/Monica20030707} | 
\href{https://monica20030707.github.io/}{monica20030707.github.io/}} 

\vspace{-9pt}

% education section
\section*{Education}
\textbf{Bellevue College} -- BS in Computer Science -- 3.6 GPA \hfill September 2021 -- June 2025\\
\vspace{-9pt}
\begin{itemize}
  \item Award: Amazon Scholarship, Activities: Social Media Manager of Computer Science Club
\end{itemize}

\vspace{-18.5pt}

% experience section
\section*{Experience}

\textbf{Sales Specialist,} {Verizon} -- Covington, WA \hfill November 2025 -- Current \\
\vspace{-9pt}
\begin{itemize}
  \item Consistently surpassed monthly sales quotas by achieving 130\% of targets through technical product expertise and consultative solution-selling.
  \item Explain complex technical concepts, such as signal strength, coverage maps, and device compatibility, to help customers and business clients make informed decisions.
  \item Streamlined inventory workflows and device diagnostic processes, reducing wait times and improving store operational efficiency.
\end{itemize}

\textbf{Associate Full Stack Developer,} {Forge Tek Studios} -- Remote \hfill August 2025 -- Current 
\vspace{-9pt}
\begin{itemize}
  \item Managed the full production release lifecycle, including environment configs and hosting, ensuring high standards for project delivery and performance.
  \item Built and deployed production-ready applications, coordinating project requirements and design details to ensure products were completed accurately.
  \item Optimized data synchronization and rendering logic, reducing ingestion overhead by 80\%—focusing on reliability and maintainability for the end-user.
\end{itemize}

\textbf{Teaching Assistant,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- December 2024 \\
\vspace{-9pt}
\begin{itemize}
  \item Provided in-depth technical coaching on complex systems and design patterns to a classroom of 40+ students with diverse backgrounds.
  \item Facilitated workshops on technical visualization and management tools, improving foundational proficiency and assignment quality by 20\%.
  \item Mentored students on engineering principles like documentation and verification as foundational practices for building stable and secure systems.
\end{itemize}

\vspace{-18.5pt}

% projects section
\section*{Projects}

\textbf{Automated Document Generation Pipeline}{ - Python, YAML, GitHub Actions} \hfill \href{https://github.com/Monica20030707/Tex_OrangeLeaf-mcp}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Architected an automated pipeline that programmatically generates tailored technical documentation from a versioned YAML data store.
  \item Reduced manual tailoring time by 90\% by automating the data selection and document formatting process through an LLM-driven orchestration engine.
  \item Engineered automated CI/CD workflows with GitHub Actions to ensure consistent, environment-independent builds and artifact management.
\end{itemize}

\textbf{Traffic Violation Detection System}{ - AWS, JavaScript, Event-Driven Architecture} \hfill \href{https://github.com/Monica20030707/AWS_rekonigition-N-read-database}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Architected an event-driven serverless pipeline on AWS, integrating Rekognition for image analysis and SQS for decoupled, resilient message processing.
  \item Implemented pattern matching with Regex to filter and route geographic data, triggering automated notification workflows via SES.
  \item Leveraged S3 and EventBridge to build a scalable, cost-efficient solution for real-time data ingestion and automated analysis.
\end{itemize}

\vspace{-18.5pt}


% skills section
\section*{Skills}
\textbf{Languages:} Python, Java, JavaScript, SQL (MySQL), TypeScript, LaTeX, YAML, HTML, CSS\\
\textbf{Skills:} Technical Support, Consultative Sales, Project Coordination, Technical Documentation, Data Analysis, CI/CD\\
\textbf{Tools:} Windows/macOS/Linux, GitHub Actions, Docker, React, Node.js, CRM, AWS SQS/S3, MySQL Workbench\\

\vspace{-6.5pt}

\end{document}
