\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,            % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[colorlinks=true, linkcolor=black, urlcolor=blue]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering
\usepackage{comment}                % block comment

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=6pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Thuy Nguyen}

\vspace{5pt}

% contact information
\centerline{\href{mailto:thuybohr@gmail.com}{thuybohr@gmail.com} | 206-423-9827 |
\href{https://www.linkedin.com/in/thuy-nguyen-46505121b/}{linkedin.com/in/thuy-nguyen-46505121b}}

\centerline{\href{https://github.com/Monica20030707}{github.com/Monica20030707} | 
\href{https://monica20030707.github.io/}{monica20030707.github.io/}} 

\vspace{-9pt}

% education section
\section*{Education}
\textbf{Bellevue College} -- BS in Computer Science -- 3.6 GPA \hfill September 2021 -- June 2025\\
\vspace{-9pt}
\begin{itemize}
  \item Award: Amazon Scholarship, Activities: Social Media Manager of Computer Science Club
\end{itemize}

\vspace{-18.5pt}

% experience section
\section*{Experience}

\textbf{Sales Specialist,} {Verizon} -- Covington, WA \hfill November 2025 -- Current \\
\vspace{-9pt}
\begin{itemize}
  \item Consistently surpassed monthly sales quotas by achieving 130\% of targets through technical product expertise and consultative solution-selling.
  \item Explain technical concepts, such as bandwidth needs, signal strength, coverage maps, Wi-Fi extender logic and device compatibility to help customers make informed decisions.
  \item Support store operations by running diagnostics on devices, validating hardware issues, managing inventory workflows, and contributing to sales goals while maintaining integrity and transparency.
\end{itemize}

\textbf{Associate Full Stack Developer,} {Forge Tek Studios} -- Remote \hfill August 2025 -- Current 
\vspace{-9pt}
\begin{itemize}
  \item Delivered a production-ready application that handled high traffic volumes with minimal infrastructure costs using serverless technologies.
  \item Optimized client-side rendering and data synchronization, reducing load and ingestion overhead by 80\% through performance-sensitive UI updates.
  \item Built and deployed a production-ready full-stack component-driven React application, integrating external APIs to dynamically render real-time content.
\end{itemize}

\textbf{Teaching Assistant,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- December 2024 \\
\vspace{-9pt}
\begin{itemize}
  \item Improved student success rates by 20\% through targeted feedback and supplemental instruction in Java and SQL best practices.
  \item Managed office hours and group labs for 40+ students, adapting technical teaching methods to suit diverse student backgrounds and learning speeds.
  \item Mentored students on software engineering principles like documentation and testing (JUnit) as foundational career skills.
\end{itemize}

\vspace{-18.5pt}

% projects section
\section*{Projects}

\textbf{Resume Automation System (Tex\_OrangeLeaf-mcp)}{ - LaTeX, YAML, GitHub Actions} \hfill \href{https://github.com/Monica20030707/Tex_OrangeLeaf-mcp}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Developed an automated pipeline that generates tailored resumes and cover letters from a versioned YAML data store using LLM-driven content selection.
  \item Reduced manual resume tailoring time by 90\% by automating the data selection and document formatting process through an LLM-driven pipeline.
  \item Engineered an automated CI/CD workflow using GitHub Actions to compile LaTeX source into production-ready PDFs upon every push.
\end{itemize}

\textbf{Stock Ratio Tracker}{ - Python, React, Perspective} \hfill \href{https://github.com/Monica20030707/Trading-Dashboard_UI}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Architected a data-flow pipeline connecting Python backend calculations to a live React dashboard, increasing trader decision-making efficiency by 40\%.
  \item Used JPMorgan Chase’s open-source library called Perspective to generate interactive graphs for real-time trader monitoring.
  \item Implemented automated unit tests to ensure ratio calculation correctness and system reliability.
\end{itemize}

\vspace{-18.5pt}


% skills section
\section*{Skills}
\textbf{Languages:} Python, Go, TypeScript, Java, JavaScript, SQL, LaTeX, YAML, HTML, CSS\\
\textbf{Skills:} Outbound Sales, Account Management, Consulting, Full-stack, RESTful APIs, CI/CD, Unit Testing\\
\textbf{Tools:} CRM, AI Tools (Gemini, Copilot), GitHub Actions, React, Node.js, Docker, AWS, MySQL\\

\vspace{-6.5pt}

\end{document}
