\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,            % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[colorlinks=true, linkcolor=black, urlcolor=blue]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering
\usepackage{comment}                % block comment

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=6pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Thuy Nguyen}

\vspace{5pt}

% contact information
\centerline{\href{mailto:thuybohr@gmail.com}{thuybohr@gmail.com} | 206-423-9827 |
\href{https://www.linkedin.com/in/thuy-nguyen-46505121b/}{linkedin.com/in/thuy-nguyen-46505121b}}

\centerline{\href{https://github.com/Monica20030707}{github.com/Monica20030707} | 
\href{https://monica20030707.github.io/}{monica20030707.github.io/}} 

\vspace{-9pt}

% education section
\section*{Education}
\textbf{Bellevue College} -- BS in Computer Science -- 3.6 GPA \hfill September 2021 -- June 2025\\
\vspace{-9pt}
\begin{itemize}
  \item Award: Amazon Scholarship, Activities: Social Media Manager of Computer Science Club
\end{itemize}

\vspace{-18.5pt}

% experience section
\section*{Experience}

\textbf{Sales Specialist,} {Verizon} -- Covington, WA \hfill November 2025 -- Current \\
\vspace{-9pt}
\begin{itemize}
  \item Consistently surpassed monthly sales quotas by achieving 130\% of targets through technical product expertise and consultative solution-selling.
  \item Explain complex technical concepts, such as network topology and device compatibility, to help customers make informed decisions in a fast-paced environment.
  \item Conduct hardware diagnostics and validate firmware issues to ensure system reliability and long-term customer success.
\end{itemize}

\textbf{Teaching Assistant,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- December 2024 \\
\vspace{-9pt}
\begin{itemize}
  \item Provided in-depth technical coaching and procedural support on complex systems to a classroom of 40+ students with diverse backgrounds.
  \item Facilitated workshops for technical visualization and management, improving success rates and foundational proficiency by 20\%.
  \item Mentored students on engineering principles like verification and documentation as foundational practices for building stable and secure systems.
\end{itemize}

\textbf{Associate Full Stack Developer,} {Forge Tek Studios} -- Remote \hfill August 2025 -- Current 
\vspace{-9pt}
\begin{itemize}
  \item Built and deployed production-ready applications, integrating external APIs to dynamically render real-time content while maintaining high standards for performance.
  \item Optimized data synchronization and rendering logic, reducing ingestion overhead by 80\% to support high-traffic, performance-sensitive environments.
  \item Owned the end-to-end development lifecycle of technical projects, ensuring reliability and maintainability for real-world users.
\end{itemize}

\vspace{-18.5pt}

% projects section
\section*{Projects}

\textbf{Automated Document Generation Pipeline}{ - Python, YAML, GitHub Actions} \hfill \href{https://github.com/Monica20030707/Tex_OrangeLeaf-mcp}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Architected an automated pipeline using Python and YAML to dynamically tailor technical documentation based on targeted requirement analysis.
  \item Reduced manual tailoring time by 90\% by automating the data selection and document formatting process through an LLM-driven orchestration engine.
  \item Engineered automated CI/CD workflows with GitHub Actions to ensure consistent, environment-independent builds and artifact management.
\end{itemize}

\textbf{Traffic Violation Detection System}{ - AWS, JavaScript, Event-Driven Architecture} \hfill \href{https://github.com/Monica20030707/AWS_rekonigition-N-read-database}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Architected an event-driven serverless pipeline on AWS, integrating Rekognition for image analysis and SQS for decoupled, resilient message processing.
  \item Implemented pattern matching with Regex to filter and route geographic data, triggering automated notification workflows.
  \item Leveraged S3, EventBridge, and Lambda to build a scalable solution for real-time data ingestion and analysis.
\end{itemize}

\vspace{-18.5pt}


% skills section
\section*{Skills}
\textbf{Languages:} Python, Java, JavaScript, SQL, PowerShell, TypeScript, LaTeX, YAML\\
\textbf{Skills:} Consultative Sales, Procedural Support, Technical Coaching, Cloud Architecture (AWS), CI/CD, Problem Solving\\
\textbf{Tools:} CRM (Salesforce), Windows/macOS/Linux, GitHub Actions, Docker, React, Node.js, AWS Rekognition\\

\vspace{-6.5pt}

\end{document}
