\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,            % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[colorlinks=true, linkcolor=black, urlcolor=blue]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering
\usepackage{comment}                % block comment

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=6pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Thuy Nguyen}

\vspace{5pt}

% contact information
\centerline{\href{mailto:thuybohr@gmail.com}{thuybohr@gmail.com} | 206-423-9827 |
\href{https://www.linkedin.com/in/thuy-nguyen-46505121b/}{linkedin.com/in/thuy-nguyen-46505121b}}

\centerline{\href{https://github.com/Monica20030707}{github.com/Monica20030707} | 
\href{https://monica20030707.github.io/}{monica20030707.github.io/}} 

\vspace{-9pt}

% education section
\section*{Education}
\textbf{Bellevue College} -- BS in Computer Science -- 3.6 GPA \hfill September 2021 -- June 2025\\
\vspace{-9pt}
\begin{itemize}
  \item Award: Amazon Scholarship, Activities: Social Media Manager of Computer Science Club
\end{itemize}

\vspace{-18.5pt}

% experience section
\section*{Experience}

\textbf{Associate Full Stack Developer,} {Forge Tek Studios} -- Remote \hfill August 2025 -- Current 
\vspace{-9pt}
\begin{itemize}
  \item Built and deployed a production-ready full-stack React application, integrating external APIs to dynamically render real-time content for real customers.
  \item Optimized client-side rendering and data synchronization, reducing load and ingestion overhead by 80\% while focusing on performance-sensitive UI updates.
  \item Managed the full production release lifecycle, including build pipelines, environment configurations, and hosting to deliver high-quality, maintainable software.
\end{itemize}

\textbf{Full Stack Developer Intern,} {METY Technology} -- Remote \hfill September 2024 -- June 2025 
\vspace{-9pt}
\begin{itemize}
  \item Engineered a real-time application using React and TensorFlow.js, processing live input and rendering responsive UI feedback to improve user interaction.
  \item Developed secure RESTful APIs with Node.js and Express.js to manage data flow, utilizing Redux Toolkit for efficient state management and Tailwind CSS for styling.
  \item Maintained a CI/CD pipeline using AWS Amplify, ensuring high-quality delivery through automated testing with Jest and code quality enforcement via ESLint.
\end{itemize}

\textbf{Open-Source Intern,} {CodeDay} -- Seattle, WA \hfill April 2025 -- May 2025 \\
\vspace{-9pt}
\begin{itemize}
  \item Led team progress as Scrum Master, ensuring timely delivery through cross-functional collaboration and clear communication with stakeholders.
  \item Resolved technical tickets in an Agile environment through the implementation of comprehensive database test cases and debugging.
  \item Leveraged Docker for containerization, ensuring consistent functionality and performance across diverse development and production environments.
\end{itemize}

\textbf{Teaching Assistant,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- December 2024 \\
\vspace{-9pt}
\begin{itemize}
  \item Guided 40+ students in Java and SQL, emphasizing clean, maintainable code and systematic problem-solving through relational database design and testing.
  \item Collaborated with faculty to refine instructional materials and provided 1:1 mentorship to enhance student proficiency in unit testing and documentation.
\end{itemize}

\begin{comment}
\textbf{Sales Specialist,} {Verizon} -- Covington, WA \hfill November 2025 -- Current \\
\vspace{-9pt}
\begin{itemize}
  \item Explain technical concepts, such as bandwidth needs, signal strength, coverage maps, Wi-Fi extender logic and device compatibility to help customers make informed decisions.
  \item Support store operations by running diagnostics on devices, validating hardware issues, managing inventory workflows, and contributing to sales goals while maintaining integrity and transparency.
\end{itemize}
\end{comment}

\begin{comment}
\textbf{Coding Competition Developer,} {Bellevue College} -- Bellevue, WA \hfill April 2024 -- May 2025 \\
\vspace{-9pt}
\begin{itemize}
  \item Developed real-time score updates using SQL and PHP, increasing efficiency by 40\%.
  \item Enhanced web interfaces with HTML and CSS, boosting user satisfaction by 30\%.
  \item Created coding problems with auto test cases for Java, Python, C++, and Golang.
  \item Assisted onsite at a competition with 30+ participants to ensure smooth operations.
\end{itemize}
\end{comment}

\vspace{-18.5pt}

% projects section
\section*{Projects}

\textbf{Stock Ratio Tracker}{ - Python, React, Typescript} \hfill \href{https://github.com/Monica20030707/tradingDashboard-UI}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Architected a real-time data-flow pipeline connecting a Python backend to a live React dashboard, ensuring stable, low-latency updates for critical metrics. 
  \item Utilized open-source visualization libraries to generate dynamic, user-focused feeds that simplify complex data monitoring.
\end{itemize}

\textbf{Traffic Violation Detection System}{ - Javascript, AWS Cloud Services} \hfill \href{https://github.com/Monica20030707/AWS_rekonigition-N-read-database}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Engineered an automated processing system using AWS S3 and EventBridge to identify and route specific data patterns from image uploads.
  \item Leveraged cloud-native services to build a scalable and reliable event-driven architecture, solving complex problems related to real-time data handling.
\end{itemize}

\vspace{-18.5pt}


% skills section
\section*{Skills}
\textbf{Languages:} TypeScript, JavaScript, Python, Java, SQL (MySQL), Go, C++, HTML/CSS\\
\textbf{Skills:} React, Node.js, RESTful APIs, Full-stack Development, Clean Code, CI/CD, Agile/Scrum\\
\textbf{Tools:} Gen AI/ML, AWS Cloud Services, Docker, Redux Toolkit, Tailwind CSS, Jest, Jira\\

\vspace{-6.5pt}

\end{document}