\documentclass[11pt]{article}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage{XCharter}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage[colorlinks=true, linkcolor=black, urlcolor=blue]{hyperref}
\usepackage{titlesec}
\raggedright
\pagestyle{empty}
\usepackage{comment}

\input{glyphtounicode}
\pdfgentounicode=1

\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=6pt}

\begin{document}

\centerline{\Huge Thuy Nguyen}
\vspace{5pt}
\centerline{\href{mailto:thuybohr@gmail.com}{thuybohr@gmail.com} | 206-423-9827 | \href{https://www.linkedin.com/in/thuy-nguyen-46505121b/}{linkedin.com/in/thuy-nguyen-46505121b}}
\centerline{\href{https://github.com/Monica20030707}{github.com/Monica20030707} | \href{https://monica20030707.github.io/}{monica20030707.github.io/}}

\vspace{-9pt}
\section*{Education}
\textbf{Bellevue College} -- BS in Computer Science -- 3.6 GPA \hfill September 2021 -- June 2025\\
\vspace{-9pt}
\begin{itemize}
  \item Award: Amazon Scholarship, Activities: Social Media Manager of Computer Science Club
\end{itemize}

\vspace{-18.5pt}
\section*{Experience}

\textbf{Associate Full Stack Developer,} {Forge Tek Studios} -- Remote \hfill August 2025 -- Current
\vspace{-9pt}
\begin{itemize}
  \item Built a production-ready component-driven React application, integrating external APIs to dynamically render real-time content and reducing ingestion overhead by 80\%.
  \item Optimized client-side rendering for performance-sensitive UI updates, ensuring stable and intuitive user interactions for real-time dashboards.
  \item Managed the full production release lifecycle, including environment configs and hosting for high visitor traffic.
\end{itemize}

\textbf{Full Stack Developer Intern,} {METY Technology} -- Remote \hfill September 2024 -- June 2025
\vspace{-9pt}
\begin{itemize}
  \item Engineered an interaction-driven application using React and TensorFlow.js, processing live camera input and rendering responsive UI feedback for real-time visualization.
  \item Developed secure RESTful APIs to manage complex data streams and backend communication.
  \item Maintained a CI/CD pipeline using AWS Amplify with automated testing to ensure product reliability.
\end{itemize}

\textbf{Web Design Intern,} {RSVP} -- Sai Gon, Vietnam \hfill July 2022 -- September 2022 \\
\vspace{-9pt}
\begin{itemize}
  \item Designed Figma mock-ups for a landing page refresh, translating user workflows into intuitive UX/UI designs.
  \item Collaborated with a team of developers to bridge design-to-code gaps and handle minor coding tickets.
  \item Shadowed users and worked with clients to ensure UI prototypes met operational needs and design standards.
\end{itemize}

\textbf{Open-Source Intern,} {CodeDay} -- Seattle, WA \hfill April 2025 -- May 2025 \\
\vspace{-9pt}
\begin{itemize}
  \item Led team progress as Scrum Master, coordinating client communications and iterating on feature design.
  \item Resolved UI tickets in an Agile environment and verified functionality through cross-environment testing.
\end{itemize}

\vspace{-18.5pt}
\section*{Projects}

\textbf{Stock Ratio Tracker}{ - Python, React, Typescript} \hfill \href{https://github.com/Monica20030707/tradingDashboard-UI}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Architected a data-flow pipeline to a live React dashboard using the Perspective library to visualize real-time data feeds for traders.
  \item Focused on situational awareness and clarity by creating stable, low-latency graph updates.
\end{itemize}

\textbf{Traffic Violation Detection System}{ - Javascript, AWS Cloud Services} \hfill \href{https://github.com/Monica20030707/AWS_rekonigition-N-read-database}{github.com} \\
\vspace{-9pt}
\begin{itemize}
  \item Developed a real-time detection and alerting system using AWS Rekognition and EventBridge.
  \item Designed the automated workflow for sending immediate notifications based on real-time data ingestion.
\end{itemize}

\vspace{-18.5pt}
\section*{Skills}
\textbf{Languages:} TypeScript, JavaScript (ES6+), HTML5, CSS3, Tailwind CSS, Python, Java, SQL, D3.js\\
\textbf{Skills:} UX/UI Design, Prototyping (Figma), Real-time Visualization, HMI Design, Component Libraries, Agile\\
\textbf{Tools:} React, Redux Toolkit, Node.js, AWS Cloud Services, Docker, Git, WebSockets, Plotly, Recharts\\

\vspace{-6.5pt}
\end{document}
